### 2023-02-02 Code/Manuscript_figures.Rmd
all code and figures

---
title: "Inc COVID-19 Case Forecast Eval: Results"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE,message=FALSE)

library(tidyverse)
library(tidytext)
library(ggrepel)

library(gridExtra)
library(cowplot)
library(ggpubr)
library(scales)

library(scoringutils)
library(viridis)

library(ggeffects)
library(emmeans)
library(splines)

setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")
cut_date <-as.Date("2021-12-21")

### Need functions
source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage

## Standardized formatting
strip.background_standard <-element_blank()
strip.text_standard <-element_text(size = 12, face='bold')
legend.text_standard <-element_text(size=12)
plot.caption_standard <-element_text(size=10, face = "italic")
axis.title.y_standard <-element_text(margin = margin(1, 10, 1, 1), size=12)
axis.text_standard <-element_text(size=11)

```

## Main Text Figures

### Figure 1. Select ensemble forecasts

```{r Fig1, echo=FALSE, warning=F, message=F, fig.height=6.5, fig.width=6.5}
### Reported cases over time
source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/reported cases.R") #reported cases
obs_data <-rd_obs() %>%
  filter(nchar(location) < 3) %>%
  filter(date <= (cut_date+4)+(7*3)) %>%
  mutate(true_value=ifelse(true_value <=0, NA, true_value),
         true_value.pop=ifelse(is.na(true_value), NA, true_value.pop))

Fig1.A <-ggplot() +
  geom_line(data=filter(obs_data, grouping=="State/Territory/DC"), 
            mapping=(aes(date, true_value.pop, group=location_name, color=grouping)), size=0.85) +
  scale_x_date(date_labels="%b-%y", breaks = obs_data$date, date_breaks ="3 months", date_minor_breaks ="1 month") +
  geom_line(data=filter(obs_data, grouping=="National"), 
            mapping=(aes(date, true_value.pop, group=location_name, color=grouping)), size=1.25) +
  geom_vline(xintercept = as.numeric(cut_date),  linetype=4, size=1.05) +
  scale_colour_manual(name="",
                      values = c("National"="black",
                                 "State/Territory/DC"="grey75")) +
  labs(title = "A. Reported Cases Per 100K Population",
       y = "Incident COVID-19 Cases") +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        legend.position = c(0.02, 0.82),legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.5,1,1,1)),
        legend.key = element_rect(colour = NA, fill = NA)) + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")

cast_dates <-dat_US_state %>% 
  filter(model=="COVIDhub-4_week_ensemble") %>% 
  ungroup() %>% 
  dplyr::select(sub_date) %>% 
  unique() %>% 
  arrange() %>%
  slice(which(row_number() %% 6 == 1))

Fig1.B <-dat_US_state %>%
  filter(sub_date <= cut_date) %>%
  filter(location=="US", 
         model=="COVIDhub-4_week_ensemble") %>% 
  filter(sub_date %in% cast_dates$sub_date) %>%
  mutate(value = case_when(quantile==0.5 ~ round(value),
                             quantile<0.5 ~ floor(value),
                             quantile>0.5 ~ ceiling(value),
                             type=='point' ~ round(value)), 
         model=as.factor(model), 
         model=droplevels(model)) %>% 
  pivot_wider(names_from = c(type, quantile), values_from=value) %>%
  rename(point = point_NA) %>% 
  ungroup() %>%
  ggplot(.) +
  geom_line(data=filter(obs_data, grouping=="National"), mapping=aes(x=date, y=true_value), color="grey85") +
  geom_point(data=filter(obs_data, grouping=="National"), mapping=aes(x=date, y=true_value), color="grey75") +
  geom_line(aes(target_end_date, point, group=interaction(sub_date, model), color=model), size=1.05) + 
  geom_point(aes(target_end_date, point, color=model), size=1.25) +
  geom_ribbon(aes(x=target_end_date, ymin=quantile_0.025, ymax=quantile_0.975,
                  fill=model, group=interaction(sub_date, model)), alpha=0.25) +
  geom_vline(xintercept = as.numeric(cut_date),  linetype=4, size=1.05) +
  scale_colour_manual(name="",
                      values = c("COVIDhub-4_week_ensemble"="#1b7837")) +
  scale_fill_manual(name="",
                    values = c("COVIDhub-4_week_ensemble"="#1b7837")) +
   scale_x_date(date_labels="%b-%y", breaks = obs_data$date, date_breaks ="3 months", date_minor_breaks ="1 month") +
  labs(title="B. Select National forecasts",
       y="Incident COVID-19 Cases") +
  theme_bw() +
  theme(axis.title.x = element_blank(), axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5),
        legend.title = element_blank(), legend.position = c(0.20, 0.82)) + scale_y_continuous(label=comma,
                                                                                               breaks=pretty_breaks(2))
plot_grid(Fig1.A, Fig1.B,
          nrow=2)

```

Figure 2. 95% coverage and relWIS  and submissions per team

```{r echo=FALSE, warning=FALSE, message=FALSE}

## WIS estimates

mean_WIS <-function() {
  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.rdata")

  ## National
  WIS_nat <-WIS_all %>%
    ungroup() %>%
    filter(location_name=="National") %>%
    summarise_scores(by = c("model"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill) %>%
    mutate(model_reorder=model) %>%
    rename(`National Forecasts`=scaled_rel_skill) 
  WIS_nat <-WIS_nat[, c(1, 3, 2)]

  ## State/Territory/District 
  WIS_state <-WIS_all %>%
    filter(location_name!="National") %>% 
    summarise_scores(by = c("model"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill) %>%
    rename(`State/Territory/DC Forecasts`=scaled_rel_skill) %>%
    mutate(model_reorder=fct_reorder(model, `State/Territory/DC Forecasts`))

  WIS_levels <-levels(WIS_state$model_reorder)

  mean_WIS <-WIS_state %>%

    full_join(., WIS_nat) %>% 
    mutate(model_reorder=factor(model, levels = WIS_levels)) %>%
    arrange(`State/Territory/DC Forecasts`) %>% 
    gather(key, value, -model, -model_reorder) %>%
    mutate(key=factor(key, levels = c("National Forecasts", 
                                      "State/Territory/DC Forecasts"))) %>% 
      mutate(value_display=format(round(value, digits=2), nsmall = 2),
             value_display=ifelse(value_display=="  NA", NA, value_display))

  }
mean_WIS <-mean_WIS()
mean_WIS$model_reorder <-fct_rev(mean_WIS$model_reorder)
mean_WIS$key <-fct_rev(mean_WIS$key)
levels_model <-levels(mean_WIS$model_reorder)
levels_key <-levels(mean_WIS$key)

WIS.heatmap <-mean_WIS %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=value)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 1.0, na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="Relative Weighted Interval Score") +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), axis.text.y=element_blank(),
        axis.text=axis.text_standard,
        legend.position="bottom")

############################################################################
############################################################################

### Coverage estimates

cov.95 <-function() {

  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")

  coverage_US <- dat_US_state %>%
    filter(sub_date <= cut_date) %>%
    filter(location=="US") %>%
    coverage(df=.) %>%
    group_by(model) %>%
    summarize(`National Forecasts`=mean(coverage.95))

  ## State/Territory/District 
  coverage_state <- dat_US_state %>%
    filter(sub_date <= cut_date) %>%
    filter(location!="US") %>%
    coverage(df=.) %>%
    group_by(model) %>%
    summarize(`State/Territory/DC Forecasts`=mean(coverage.95))

  cov.95 <-coverage_US %>%
    full_join(., coverage_state, by="model") %>%
    gather(key, value, -model) %>%
    mutate(cov_diff=abs(0.95-value)) %>%
    mutate(value_display=format(round(value, digits=2), nsmall = 2),
           value_display=ifelse(value_display=="  NA", NA, value_display))
}

cov.95 <-cov.95() %>%
  mutate(model_reorder=factor(model, levels=levels_model), 
         key=factor(key, levels=levels_key))

cov.heatmap <-cov.95 %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=value)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "white", mid = "#f7fcb9", high = "#31a354", midpoint = 0.75, na.value = "grey75") +
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="95% Coverage") +
  theme(axis.title.x = element_blank(), #axis.text.x = element_text(angle = 45, hjust=1),
        axis.title.y = element_blank(), axis.text.y=element_blank(),
        axis.text=axis.text_standard,
        legend.position="bottom")

############################################################################
############################################################################

### Submissions over time

submissions <-function(df) {

  start_date <-as.Date("2020-07-28")
  stop_date <-as.Date("2022-02-22")

  df <-df %>%
    filter(sub_date >= start_date & sub_date <= cut_date) %>% #stop_date) %>%
    dplyr::select(forecast_date, model, location, target, sub_date) %>%
    distinct() %>%
    dplyr::select(-target) %>%
    distinct() %>%
    group_by(sub_date, model) %>%
    summarize(locs=n()) %>%
    ungroup() %>%
    mutate(total_sub=length(unique(sub_date))) %>%
    group_by(model) %>%
    mutate(wks_sub=length(sub_date),
           per_sub=(wks_sub/total_sub)) %>%
    ungroup() %>%
  dplyr::select(-locs, -sub_date) %>%
  distinct()

  return(df)

}

all_dat <-function(){

  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_2021-03-13.Rdata")
  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_2022-03-21.Rdata")

  all_dat <-all_dat %>%
    bind_rows(., all_dat_updated) %>%
    mutate(model=ifelse(sub_date < "2021-03-16" & model=="COVIDhub-ensemble", "COVIDhub-4_week_ensemble", model))
}
all_dat <-all_dat()
subs_nat <-submissions(df=filter(all_dat, location=="US")) %>% 
  filter(model %in% mean_WIS$model[mean_WIS$key=="National Forecasts" & !is.na(mean_WIS$value)]) %>%
  mutate(key="National Forecasts")
subs_state <-submissions(df=filter(all_dat, location!="US")) %>% 
  filter(model %in% mean_WIS$model[mean_WIS$key=="State/Territory/DC Forecasts"]) %>%
  mutate(key="State/Territory/DC Forecasts")

missings <-mean_WIS %>%
  filter(is.na(value)) %>%
  rename(per_sub=value)

all_subs <-subs_nat %>%
  bind_rows(., subs_state) %>% 
  mutate(model_reorder=factor(model, levels=levels_model), 
         key=factor(key, levels=levels_key),
         value_display=format(round(per_sub, digits=2), nsmall = 2),
         value_display=ifelse(value_display=="  NA", NA, value_display)) %>%
  bind_rows(., missings) %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=per_sub)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient(low = "#fde0dd", high = "#c51b8a", na.value = "grey75") +
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="% Weeks \nSubmitted") +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        axis.text=axis.text_standard,
        legend.position="bottom")

############################################################################
############################################################################

```

``` {r Fig 2, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=12}

plot_grid(all_subs, WIS.heatmap, cov.heatmap,
          nrow=1, 
          rel_widths = c(1, 0.6, 0.6))

```

### Figure 3. Coverage.

```{r echo=FALSE, warning=F, message=F, fig.show='hide'}

# Read in and manipulate data + plot structure
cov.fig_dat <-function(df) {
  coverage <-df %>%
    coverage(df=.) %>%
    group_by(model) %>%
    summarize(coverage.95=mean(coverage.95),
              coverage.80=mean(coverage.80),
              coverage.50=mean(coverage.50)) %>%
    gather("expected_cov", "observed_cov", coverage.95:coverage.50) %>%
    mutate(expected_cov=gsub("coverage.", "", expected_cov),
           expected_cov=as.numeric(expected_cov),
           expected_cov=expected_cov/100,
           bold=ifelse(model=="COVIDhub-baseline" | model=="COVIDhub-4_week_ensemble", "T", "F"),
          grouping=ifelse(model=="COVIDhub-baseline", "COVIDhub-baseline", 
                           ifelse(model=="COVIDhub-4_week_ensemble", "COVIDhub-4_week_ensemble", "Other teams")))
  return(coverage)
}
data_labels <-function(df) {

  ensemble_cov <-df%>%
    filter(model=="COVIDhub-4_week_ensemble")

  data_labels <-df %>%  
    filter(model!="COVIDhub-4_week_ensemble") %>%
    mutate(test_95=ifelse(expected_cov==0.95 & observed_cov > ensemble_cov$observed_cov[ensemble_cov$expected_cov==0.95], 1, NA),
           test_80=ifelse(expected_cov==0.80 & observed_cov > ensemble_cov$observed_cov[ensemble_cov$expected_cov==0.80], 1, NA),
           test_50=ifelse(expected_cov==0.50 & observed_cov > ensemble_cov$observed_cov[ensemble_cov$expected_cov==0.50], 1, NA)) %>%
    filter(!is.na(test_95) | !is.na(test_80) | !is.na(test_50)) %>%
    group_by(model) %>%
    mutate(model_count=n()) %>%
    filter(model_count==3 & expected_cov==0.95) %>%
    mutate(model=ifelse(model=="JHU_UNC_GAS-StatMechPool", "JHU_UNC_GAS\n-StatMechPool", model)) %>%
    mutate(model=ifelse(model=="MOBS-GLEAM_COVID", "MOBS-GLEAM_\nCOVID", model)) %>%
     mutate(model=ifelse(model=="IEM_MED-CovidProject", "IEM_MED\n-CovidProject", model)) %>%
  return(data_labels)
  }
cov.plot <-function(df, df2) {
  ggplot(df) +
    geom_line(data=filter(df, bold=="F"), 
              mapping=aes(expected_cov, observed_cov, group=model, color=grouping, size=bold, alpha=0.75)) +
    geom_point(data=filter(df, bold=="F"), 
               mapping=aes(expected_cov, observed_cov, group=model, color=grouping), size=1.5) +
    geom_line(data=filter(df, bold=="T"), 
              mapping=aes(expected_cov, observed_cov, group=model, color=grouping, size=bold, alpha=0.75)) +
    geom_point(data=filter(df, bold=="T"), 
               mapping=aes(expected_cov, observed_cov, group=model, color=grouping), size=3) +
    geom_line(aes(expected_cov, expected_cov, color=grouping, group=model), linetype="dashed", size=1.5, color="black") +
    scale_size_manual(values = c("T"=1.5, "F"=0.85)) +
    scale_colour_manual(values = c("COVIDhub-baseline"="#762a83",
                                   "COVIDhub-4_week_ensemble"="#1b7837",
                                   "Other teams"="grey75"),
                        labels=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week_ensemble"),
                        breaks=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week_ensemble")) +
    guides(size = "none", alpha="none") +
    labs(y="Observed Coverage") +
    theme_bw()  + 
    theme(legend.position = "none", 
          axis.title.x = element_blank()) +
    geom_text_repel(data=df2,
                    mapping=aes(expected_cov, observed_cov, label=model), size=3,
                    force=1, point.padding=unit(0.5,'lines'), nudge_x =0.1,
                    segment.size= 0.05,  segment.color="grey50",
                    direction="y", #hjust = "right",
                    vjust=0.5) +
    scale_x_continuous(expand = expansion(mult = c(0.05, 0.25)))
}

# Figures
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")

coverage_US <-cov.fig_dat(filter(dat_US_state, location=="US", sub_date <= cut_date))
labels_US <-data_labels(coverage_US)
Cov.Nat <-cov.plot(coverage_US, labels_US) +
  theme(legend.position = c(0.02, 0.88), legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.5,1,1,1)),
        legend.key = element_rect(colour = NA, fill = NA)) +
  labs(title="A. Coverage for National Forecasts")

coverage_states <-cov.fig_dat(filter(dat_US_state, location!="US", sub_date <= cut_date))
labels_states <-data_labels(coverage_states)
Cov.State <-cov.plot(coverage_states, labels_states) +
  labs(title="B. Coverage for National State/Territory/DC Forecasts")

# Largest Counties
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date))
labels_count <-data_labels(coverage_count) 
Cov.Co <-cov.plot(coverage_count, labels_count) +
  labs(title="C. Coverage for Large County Forecasts*",
       x="Expected Coverage")

Fig3 <-annotate_figure(
  grid.arrange(Cov.Nat, Cov.State, Cov.Co, ncol=1),
  bottom = text_grob("*U.S. counties with a population of at least 93,230 people ", hjust=1, x=1, face = "italic", size = 10))

```

```{r Fig3, echo=FALSE, warning=F, message=F, fig.height=15, fig.width=6}

Fig3

```

### Figure 4. Relative WIS Across Geospatial Units

```{r Fig4, echo=FALSE, warning=F, message=F, fig.height=8, fig.width=6.5}

# All counties
relWIS_co <-function(){

  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.rdata")

  rel_WIS_large_co <-WIS_all %>%
    summarise_scores(by = c("model"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill) %>%
    distinct() %>%
    mutate(geo_scale="County forecasts: Size Quantile 5 (Largest)")

  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_non large counties_all.Rdata")
  rel_WIS_co <-WIS_all %>%
    ungroup() %>%
    summarise_scores(by = c("model", "pop_size_quant2"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill, pop_size_quant2) %>%
    mutate(geo_scale=ifelse(pop_size_quant2==1, "County Forecasts: Size Quantile 1 (Smallest)",
                            ifelse(pop_size_quant2==2, "County Forecasts: Size Quantile 2",
                                   ifelse(pop_size_quant2==3, "County Forecasts: Size Quantile 3", "County Forecasts: Size Quantile 4" 
                                          #"County forecasts: Size Quantile 5 (Largest)"
                                          )))) %>%
    dplyr::select(-pop_size_quant2) %>%
    bind_rows(., rel_WIS_large_co)
}
relWIS_co <-relWIS_co()
models_include_co <-relWIS_co %>%
  filter(geo_scale=="County Forecasts: Size Quantile 1 (Smallest)") %>%
  dplyr::select(model, geo_scale) %>%
  distinct()

# Merge
models_include <-mean_WIS %>% 
  dplyr::select(-value_display, 
                -model_reorder) %>%
  spread(key,value) %>%
  drop_na()

relWIS_all <-mean_WIS %>%
  rename(scaled_rel_skill=value,
         geo_scale=key) %>%
  mutate(geo_scale=as.character(geo_scale)) %>% 
  bind_rows(., relWIS_co) %>%
  filter(model %in% models_include_co$model) %>%
  mutate(model_reorder=factor(model, levels=levels_model))

relWIS_all$geo_scale <-factor(relWIS_all$geo_scale, levels = c("County Forecasts: Size Quantile 1 (Smallest)", 
                                                               "County Forecasts: Size Quantile 2", 
                                                               "County Forecasts: Size Quantile 3", 
                                                               "County Forecasts: Size Quantile 4", 
                                                               "County forecasts: Size Quantile 5 (Largest)",
                                                               "State/Territory/DC Forecasts", "National Forecasts"))

# Colors
my_colors <-viridis(6) 
my_colors <-my_colors[-(6)] #removes the yellow color, which can be hard to see 
my_colors <-c(my_colors, "#d01c8b", "#f1b6da")

Fig4.B <-relWIS_all %>%
  mutate(model_reorder = fct_rev(model_reorder)) %>%
  filter(model!="COVIDhub-baseline") %>%
  ggplot(., aes(model_reorder, scaled_rel_skill)) +
  geom_hline(yintercept = 1, linetype="dashed") +
  geom_point(aes(color=geo_scale), size=4, alpha=0.85, 
             position = position_dodge(width = 0.2)) + 
  scale_color_manual(values=my_colors) +
  labs(y="Relative Weighted Interval Score" , 
       ) +
  theme_bw() +
      theme(axis.text.x =element_text(size=11, angle = 45, hjust=1), axis.text=axis.text_standard,
        axis.title.x = element_blank(), 
        legend.margin=margin(c(0.25,0.25,0.25,0.25)),
        legend.justification = c(0, 0.5),
        legend.key = element_rect(colour = NA, fill = NA), 
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.position = "bottom", 
        plot.caption = plot.caption_standard) +
 scale_y_continuous(expand = expansion(mult = c(0.05, 0.05))) + guides(color=guide_legend(nrow=4, byrow=TRUE))

Fig4.B

```

### Figure 5. RelWIS per state/territory

```{r Fig5, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=9}

# Forecasts
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")

relWIS <-WIS_all %>%
    summarise_scores(by = c("model", "location_name"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
  mutate(scaled_rel_skill=round(scaled_rel_skill, 1),
         log_WIS=log2(scaled_rel_skill),
         location_name=as.character(location_name))

Locations <-relWIS %>%
  dplyr::select(location_name) %>%
  distinct()

Models <-relWIS %>%
  dplyr::select(model) %>%
  distinct()

Locations_models <-crossing(Locations, Models) 
relWIS <- Locations_models %>%
  left_join(., relWIS) %>%
  mutate(model_reorder=factor(model, levels=levels_model))

# Reorder x and y axes
relWIS$location_name <-as.factor(relWIS$location_name)
relWIS$location_name <-relevel(relWIS$location_name, ref="National")
relWIS$location_name <-fct_rev(relWIS$location_name)

# Figure
relWIS$model_reorder <-fct_rev(relWIS$model_reorder)
ggplot(relWIS, aes(model_reorder, location_name)) +
  geom_tile(aes(fill=log_WIS)) +
  geom_text(aes(label=scaled_rel_skill), size=3) +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 0, na.value = "grey75", 
                       name = "Relative\nWeighted Interval Score", 
                       breaks = c(-1,0,1,2), 
                       labels =c("0.5", 1, 2, 3)) + 
  theme_bw() +
  labs(fill="Relative Weighted Interval Score") +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1),
        axis.title.y = element_blank(),
        axis.text=axis.text_standard, plot.caption = plot.caption_standard)

```

### Figure 6. Absolute WIS and 95% coverage over time

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.show='hide'}

#options(scipen = 999)

# Function for WIS over time
WIS.ot.fig_dat <-function(df) {

  sub_date <-c(unique(df$sub_date))
  model <-c(as.character(unique(df$model)))
  model_dates <-crossing(sub_date, model)

  cast_dates <-df %>%
    dplyr::select(sub_date, date) %>%
    distinct() %>%
    left_join(model_dates, by="sub_date")

  dat <-df %>%
    full_join(cast_dates, ., by=c("model", "sub_date", "date")) %>%
    mutate(bold=ifelse(model=="COVIDhub-baseline" | model=="COVIDhub-4_week_ensemble", "T", "F")) %>%
    group_by(model, date, bold) %>%
    summarize(abWIS=mean(interval_score, na.rm=TRUE)) %>%
    ungroup() %>%
    mutate(grouping=ifelse(model=="COVIDhub-baseline", "COVIDhub-baseline", 
                           ifelse(model=="COVIDhub-4_week_ensemble", "COVIDhub-4_week_ensemble", "Other teams"))) #%>%
  return(dat)

}
cov.ot.fig_dat <-function(df) {

  sub_date <-c(unique(df$sub_date))
  model <-c(as.character(unique(df$model)))
  model_dates <-crossing(sub_date, model)

  cov <-df %>%
    group_by(model, target_end_date) %>%
    coverage(df=.) %>%
    summarize(cov.95=mean(coverage.95))

  dat <-df %>%
    dplyr::select(sub_date, target_end_date) %>%
    distinct() %>%
    left_join(., model_dates, by="sub_date") %>%
    dplyr::select(-sub_date) %>%
    left_join(., cov, by=c("model", "target_end_date")) %>%
    distinct() %>%
    ungroup() %>%
    mutate(grouping=ifelse(model=="COVIDhub-baseline", "COVIDhub-baseline", 
                           ifelse(model=="COVIDhub-4_week_ensemble", "COVIDhub-4_week_ensemble", "Other teams"))) %>%
    mutate(bold=ifelse(model=="COVIDhub-baseline" | model=="COVIDhub-4_week_ensemble", "T", "F"))

  return(dat)

}
ot.plot <-function(df, x, y) {

  ggplot() +
    geom_line(data=filter(df, bold=="F"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    geom_point(data=filter(df, bold=="F"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    geom_line(data=filter(df, bold=="T"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    geom_point(data=filter(df, bold=="T"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    scale_size_manual(values = c("T"=1.25, "F"=0.85)) +
    scale_x_date(date_labels="%b-%y", breaks = df$x, date_breaks ="3 months", date_minor_breaks ="1 month") +
    geom_vline(xintercept = as.numeric(cut_date),  linetype=4, size=1.05) +
    scale_colour_manual(name="",
                        values = c("COVIDhub-baseline"="#762a83",
                                   "COVIDhub-4_week_ensemble"="#1b7837",
                                   "Other teams"="grey80"),
                        labels=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week_ensemble"),
                        breaks=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week_ensemble")) +
    guides(size = "none") + 
    theme_bw() +
    theme(legend.position = "none", 
          axis.title.x = element_blank())
}

###########################################################################
############################################################################

### WIS Over time
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")

## National
WIS_ot_nat <-WIS.ot.fig_dat(filter(WIS_all, location_name=="National")) 
Fig6.A <-ot.plot(WIS_ot_nat, date, abWIS)  +
  theme(axis.title.x=element_blank(),
        legend.position = c(0.02, 0.80),legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.25,0.25,0.25,0.25)),
        legend.key = element_rect(colour = NA, fill = NA)) +
  labs(title="A. Average Weighted Interval Score for National Forecasts",
       y = "Average Weighted Interval Score") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.35))) + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5)) +
  scale_y_continuous(trans='log10')

## State/Territory/District
WIS_ot_state <-WIS.ot.fig_dat(filter(WIS_all, location_name!="National",
                                     location_name!="American Samoa"))
Fig6.B <-ot.plot(WIS_ot_state, date, abWIS) +
  labs(title = "B. Average Weighted Interval Score for State/Territory/DC Forecasts",
       y = "Average Weighted Interval Score") + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5)) +
  scale_y_continuous(trans='log10')

## Large Counties
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.Rdata")
WIS_ot_co <-WIS.ot.fig_dat(WIS_all)
Fig6.C <-ot.plot(WIS_ot_co, date, abWIS) +
  labs(title = "C. Average Weighted Interval Score for Large County Forecasts*",
       x = "Forecast target date",
       y = "Average Weighted Interval Score") + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5)) +
  scale_y_continuous(trans='log10')

############################################################################
############################################################################

### Coverage Over time

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")

## National
cov_ot_nat <-cov.ot.fig_dat(filter(dat_US_state, location=="US", sub_date <= cut_date)) 
Fig6.D <-ot.plot(cov_ot_nat, target_end_date, cov.95)  +
  geom_hline(yintercept = 0.95,  linetype=6, size=1.05) +
  theme(axis.title.x=element_blank()) +  
  labs(title="D. 95% Coverage for National Forecasts",
       y = "95% Coverage") + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

## State/Territory/District
cov_ot_state <-cov.ot.fig_dat(filter(dat_US_state, location!="US", sub_date <= cut_date))
Fig6.E <-ot.plot(cov_ot_state, target_end_date, cov.95) +
  geom_hline(yintercept = 0.95,  linetype=6, size=1.05) +
  labs(title = "E. 95% Coverage for State/Territory/DC Forecasts",
       y = "95% Coverage") + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

## Large Counties
cov_ot_co <-cov.ot.fig_dat(filter(dat_large_count, sub_date <= cut_date))
Fig6.F <-ot.plot(cov_ot_co, target_end_date, cov.95) +
  geom_hline(yintercept = 0.95,  linetype=6, size=1.05) +
  labs(title = "F. 95% Coverage for Large County Forecasts*",
       x = "Forecast target date",
       y = "95% Coverage") +  theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

############################################################################
############################################################################

wrapper <- function(x, ...) paste(strwrap(x, ...), collapse = "\n")
# The a label
teams_nat_st <-"Panels A, D, B and E include: LNQ-ens1, Microsoft_DeepSTIA, COVIDhub-4_week_ensemble, USC-SI_kJalpha, CU-select, LANL-GrowthRate, JHU_CSSE-DECOM, COVIDhub-trained_ensemble, COVIDhub-baseline, Karlen-pypm, BPagano-RtDriven, JHUAPL-Bucky, UVA-Ensemble, IEM_MED-CovidProject, CEID-Walk, Covid19Sim-Simulator, IowasStateLW-STEM, UCLA-SuEIR, JHU_IDD-CovidSP, RobertWalraven-ESG, MOBS-GLEAM_COVID, and CovidAnalytics-DELPHI. "

teams_co <-"Panels C and F include: LNQ-ens1, COVIDhub-4_week_ensemble, CU-select, LANL-GrowthRate, COVIDhub-trained_ensemble, COVIDhub-baseline, JHUAPL-Bucky, UVA-Ensemble, CEID-Walk, JHU_UNC_GAS-StatMechPoole, IowasStateLW-STEM, JHU_IDD-CovidSP, UMass-MechBayes, FAIR-NRAR, FRBSF_Wilson-Econometric."

############################################################################
############################################################################

Fig6 <-annotate_figure(
  grid.arrange(Fig6.A, Fig6.D,
               Fig6.B, Fig6.E,
               Fig6.C, Fig6.F,
             #Fig6.D, Fig6.H,
             ncol=2),
          bottom = text_grob("*U.S. counties with a population of at least 93,230 people \n", hjust=1, x=1, face = "italic", size = 10))

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

Fig6.note1 <-annotate_figure(Fig6,
                bottom = text_grob(label = wrapper(teams_nat_st, width = 195), hjust=0, x=0.001, size = 10))

```

```{r Fig6, echo=FALSE, warning=FALSE, message=FALSE, fig.height=11, fig.width=13}

annotate_figure(Fig6.note1,
                bottom = text_grob(paste0("\n", label = wrapper(teams_co, width = 195)), hjust=0, x=0.001,
                                   size = 10))

```

### Figure 7 . Marginal mean WIS

```{r echo=FALSE, warning=F, message=F}

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_gee.Rdata") # data
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/gee_for_manuscript.rda")

team <-c(unique(as.character(WIS_gee$model))) 
dat_team <-list()
means_sds <-list()
means_sds_phase <-list()

marg_means_int <-list()
marg_means <-list()

# Model Predictions 
for(i in 1:length(team)){

  dat_team[[i]] <-as.data.frame(WIS_gee %>%
                                  filter(model==team[i]) %>%
                                  mutate(model=droplevels(model)) %>%
                                  ungroup())

  means_sds[[i]] <-dat_team[[i]] %>%
    mutate(mean_log_WIS=mean(log(interval_score)),
           sd_log_WIS=sd(log(interval_score)),
           mean_log_cases=mean(log(true_value)),
           sd_log_cases=sd(log(true_value))
    ) %>%
    dplyr::select(model, contains("mean_"), contains("sd_")) %>%
    distinct()

  # Log(cases)
  marg_means_int[[i]] <-as.data.frame(emmeans(model[[i]], ~1))
  marg_means_int[[i]] <-marg_means_int[[i]] %>%
    rename(predicted=emmean) %>%
    mutate(model=team[i],
           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_lo=(asymp.LCL*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_up=(asymp.UCL*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS) %>%
    mutate(predicted_back_rescale=exp(predicted_back),
           predicted_back_lo_rescale=exp(predicted_back_lo),
           predicted_back_up_rescale=exp(predicted_back_up))

  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase")) %>% #, "cases_log_std[-2:2]")) %>%
    rename(phase=x,
           cases=group) %>%

    mutate(model=team[i],
           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_lo=(conf.low*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_up=(conf.high*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS) %>%

    mutate(predicted_back_rescale=exp(predicted_back),
           predicted_back_lo_rescale=exp(predicted_back_lo),
           predicted_back_up_rescale=exp(predicted_back_up)) 
}
marg_means_int <-do.call(rbind.data.frame, marg_means_int)
marg_means <-do.call(rbind.data.frame, marg_means)

marg_means_int <-marg_means_int %>% 
  dplyr::select(-`1`) %>%
  mutate(model=as.factor(model),
         model=fct_reorder(model, predicted_back),
         phase="Mean across phases") 
levels <-levels(marg_means_int$model)

marg_means <-marg_means %>%

  ## Order by increasing error, on average
  mutate(model=as.factor(model),
         model=factor(model, levels = levels)) %>%
  mutate(phase=as.factor(ifelse(phase=="increasing", "Increasing",
                                    ifelse(phase=="decreasing", "Decreasing",
                                           ifelse(phase=="peak", "Peak",
                                                  ifelse(phase=="nadir", "Nadir", "Mean across phases"))))),
         phase=factor(phase, 
                          levels = c("Mean across phases", "Increasing", "Peak", "Decreasing",  "Nadir"))
  ) %>%
  ungroup()

baseline <-filter(marg_means_int, model=="COVIDhub-baseline")

# Figure
Fig7A <-marg_means_int %>%
  ggplot(.) +
  geom_point(aes(model, predicted_back_rescale)) +
  geom_linerange(aes(model, ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale)) +
  geom_hline(data=baseline, mapping=aes(yintercept=baseline$predicted_back_lo_rescale), color="red", linetype="dashed") + 
  geom_hline(data=baseline, mapping=aes(yintercept=baseline$predicted_back_up_rescale), color="red", linetype="dashed") +
  labs( y="Marginal mean\n Weighted Interval Score", 
        title="A.") +
  theme_bw() +
  theme(axis.title.y=axis.title.y_standard, axis.text=axis.text_standard,
        legend.position = "bottom", legend.title = element_blank(), legend.text=legend.text_standard,
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1))

```

```{r echo=FALSE, warning=F, message=F}

Fig7B <-marg_means %>%
  mutate(scaled_pred=predicted_back/baseline$predicted_back,
         SE_scaled=(predicted_back_up-predicted_back_lo)/3.92,
         prob_base=round(pnorm(baseline$predicted_back,
                               predicted_back, SE_scaled), 5),
         prob_label=ifelse(prob_base >=0.9, "*", NA),
         phase=fct_rev(phase)) %>%
  ggplot(.) +
  geom_tile(aes(model, phase, fill=scaled_pred)) +
  geom_text(aes(model, phase, label=prob_label), size=4) +
  scale_fill_gradient2(low = "#7fcdbb", high = "#fecc5c", midpoint = 1.0,
                       name="Marginal mean Weighted Interval Score  \nscaled to the marginal mean  \nof COVIDhub-baseline model  \nacross all phases",
                       guide = guide_colourbar(barheight = 1.5)) +
  labs(y="", title="B.",
       caption="*Probability >= 0.90 that forecasts outperform baseline") + 
  theme_bw() +
  theme(legend.position = "bottom", legend.title.align=0.5, legend.box.just = "center", 
    plot.caption = plot.caption_standard,
    strip.text=strip.text_standard, strip.background=strip.background_standard,
    panel.border = element_rect(colour = "black", fill = NA),
    axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1), axis.text=axis.text_standard,
    axis.ticks.y=element_blank())

```

```{r Fig7, echo=FALSE, warning=F, message=F, fig.height=8.5, fig.width=8.5}

Fig7A_updated <-Fig7A + theme(axis.text.x = element_blank())

plot_grid(Fig7A_updated, Fig7B, rel_heights  = c(0.5, 1), axis = "l",
          align="v", nrow = 2)

```

### 2023-02-02 Code/Supplement 1A_figures.Rmd
all code and figures

---
title: "Supplement 1A"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning=FALSE,message=FALSE)

library(tidyverse)
library(tidytext)
library(ggrepel)

library(gridExtra)

library(scoringutils)
library(viridis)

library(ggeffects)
library(emmeans)
library(splines)

setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")

### Need functions
source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage
### Estimate Relative WIS 
pairWIS_fun <-function(x, df) {

  df <-df %>%
    pairwise_comparison(., summarise_by = c("model"),
                        baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill) %>%
    distinct()
}
pairWIS_co_fun <-function(x, df) {

  df <-df %>%
    pairwise_comparison(., summarise_by = c("model", "pop_size_quant2"),
                        baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, pop_size_quant2, scaled_rel_skill) %>%
    distinct()
}

## Standardized formatting
strip.background_standard <-element_blank()
strip.text_standard <-element_text(size=10, face='bold')
legend.text_standard <-element_text(size=12)
plot.caption_standard <-element_text(size=11, face = "italic")
axis.title.y_standard <-element_text(margin = margin(1, 10, 1, 1), size=12)
axis.text_standard <-element_text(size=11)

## Function for setting up legends in empty facet spaces
library(gtable)
library(cowplot)

shift_legend <- function(p){

  # check if p is a valid object
  if(!"gtable" %in% class(p)){
    if("ggplot" %in% class(p)){
      gp <- ggplotGrob(p) # convert to grob
    } else {
      message("This is neither a ggplot object nor a grob generated from ggplotGrob. Returning original plot.")
      return(p)
    }
  } else {
    gp <- p
  }

  # check for unfilled facet panels
  facet.panels <- grep("^panel", gp[["layout"]][["name"]])
  empty.facet.panels <- sapply(facet.panels, function(i) "zeroGrob" %in% class(gp[["grobs"]][[i]]))
  empty.facet.panels <- facet.panels[empty.facet.panels]
  if(length(empty.facet.panels) == 0){
    message("There are no unfilled facet panels to shift legend into. Returning original plot.")
    return(p)
  }

  # establish extent of unfilled facet panels (including any axis cells in between)
  empty.facet.panels <- gp[["layout"]][empty.facet.panels, ]
  empty.facet.panels <- list(min(empty.facet.panels[["t"]]), min(empty.facet.panels[["l"]]),
                             max(empty.facet.panels[["b"]]), max(empty.facet.panels[["r"]]))
  names(empty.facet.panels) <- c("t", "l", "b", "r")

  # extract legend & copy over to location of unfilled facet panels
  guide.grob <- which(gp[["layout"]][["name"]] == "guide-box")
  if(length(guide.grob) == 0){
    message("There is no legend present. Returning original plot.")
    return(p)
  }
  gp <- gtable_add_grob(x = gp,
                        grobs = gp[["grobs"]][[guide.grob]],
                        t = empty.facet.panels[["t"]],
                        l = empty.facet.panels[["l"]],
                        b = empty.facet.panels[["b"]],
                        r = empty.facet.panels[["r"]],
                        name = "new-guide-box")

  # squash the original guide box's row / column (whichever applicable)
  # & empty its cell
  guide.grob <- gp[["layout"]][guide.grob, ]
  if(guide.grob[["l"]] == guide.grob[["r"]]){
    gp <- gtable_squash_cols(gp, cols = guide.grob[["l"]])
  }
  if(guide.grob[["t"]] == guide.grob[["b"]]){
    gp <- gtable_squash_rows(gp, rows = guide.grob[["t"]])
  }
  gp <- gtable_remove_grobs(gp, "guide-box")

  return(gp)
}

## Change labels for counties
 rename_counts <-function(df) {   
   df <-df %>%
     mutate(pop_size_quant2=ifelse(pop_size_quant2==1, "County Forecasts: Size Quantile 1",
                                 ifelse(pop_size_quant2==2, "County Forecasts: Size Quantile 2",
                                        ifelse(pop_size_quant2==3, "County Forecasts: Size Quantile 3", 
                                               ifelse(pop_size_quant2==4, "County Forecasts: Size Quantile 4", "County forecasts: Size Quantile 5")))))
}

```

## Supplemental Figures

### Supplement 1

```{r Fig S1A, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=11}
start_date <-as.Date('2020-07-28')
stop_date <-as.Date('2021-12-21')

sec_models <-c("CU-nochange",  "CU-scenario_high", "CU-scenario_low", "CU-scenario_mid", "COVIDhub_CDC-ensemble") ## Non-primary models should be exlcuded

## Must have 4 weeks of forecasts for all locations
include_wks <-function(x, df){

  df <-df %>%
    group_by(model, sub_date, location) %>%
    mutate(no_horizons=length(unique(target))) %>% 
    ungroup() %>%
    filter(no_horizons>=4) #There should be at least 4 horizons
}

## Must have quantities for all forecasts
include_quant <-function(x, df){

  df <-df %>%
    group_by(model, location, forecast_date, target) %>%
    mutate(quants=length(quantile[!is.na(quantile)])) %>%
    ungroup() %>%
    filter(quants==7) #There should be 7 quantiles

}

## Must have forecasts for at least 50 locations for states/territories/district and national
include_locs <-function(x, df){

  df <-df %>%
    mutate(location=as.factor(location)) %>%
    group_by(model, forecast_date) %>%
    mutate(locs=length(unique(location))) %>% #[quantile==0.5 & target=="1 wk ahead inc case"]))) %>%
    ungroup() %>%
    filter(locs>=50)

}

## Must have 75% of all counties per quantile per submission date forecasted
include_locs_co <-function(x, df){

  df <-df %>%
    group_by(pop_size_quant2) %>%
    mutate(locs_total=length(unique(location))) %>% 
    ungroup() %>%
    group_by(model, pop_size_quant2, sub_date) %>%
    mutate(locs=length(unique(location))) %>% #[quantile==0.5 & target=="1 wk ahead inc case"]))) %>%
    ungroup() %>%
    mutate(percent_co=locs/locs_total) %>%
    filter(percent_co>=0.75)
}

## Must have submitted at least 50% of weeks
include_subs <-function(x, df){

  df <-df %>%
    filter(sub_date >= start_date) %>%
    mutate(total=length(unique(sub_date))) %>% 
    group_by(model) %>%
    mutate(subs=length(unique(sub_date))) %>%
    ungroup() %>%
    mutate(percent_sub=subs/total) %>%
    filter(percent_sub>=0.50)

}

############################################################################
############################################################################

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/updated_cases_nat_state_forecasts_2022-04-04.Rdata")

### National + state submissions
nat_st <-all_dat %>%
  filter(!(model %in% sec_models),
         sub_date >= start_date & sub_date <= stop_date) %>%
  filter(type=="point")

### National + state submissions that met inclusion criteria
teams_nat_st <-all_dat %>%
  filter(!(model %in% sec_models),
         sub_date >= start_date & sub_date <= stop_date) %>%
  include_quant(df=.) %>% #all quantiles present
  include_wks(df=.) %>% #all targets included 
  include_locs(df=.) %>% #at least 50 locations
  include_subs(df=.) %>% #submitted at least 50% of the time
  dplyr::select(model) %>%
  mutate(model_rename=paste0("*", model)) %>%
  distinct()

### Submission plots

nat_st %>%
  dplyr::select(-target, -target_end_date, -value) %>%
  distinct() %>%
  group_by(sub_date, model) %>%
  summarize(locs=n()) %>%
  ungroup() %>%
  mutate(log_loc=log(locs)) %>%
  ungroup() %>%
  mutate(total_sub=length(unique(sub_date))) %>%
  group_by(model) %>%
  mutate(wks_sub=length(sub_date),
         per_sub=wks_sub/total_sub) %>%
  ungroup() %>%
  left_join(., teams_nat_st, by="model") %>%
  mutate(model_rename=ifelse(is.na(model_rename), model, model_rename),
         model_rename=fct_reorder(model_rename, wks_sub)) %>%
  ggplot(., aes(sub_date, model_rename)) +
  geom_tile(aes(fill=log_loc)) +
  scale_fill_gradient(low = "#c7e9c0", high = "#41ab5d") + 
  geom_text(aes(label=locs), size=1.50) +
  scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%B") +
  theme_bw() +
  labs(title = "A. Primary Model* Submissions for National/State/Territory-Level Case Forecasts Over Time",
       subtitle= "The number of locations forecasted per submission is labled",
       caption = "*Model met inclusion criteria") +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1),
        axis.title.y = element_blank(),
        legend.position = "none")

```

### 2023-02-02 Code/Supplement 1B_figures.Rmd
all code and figures

--- 2023-02-02 Code/Supplement 1A_figures.Rmd
@@
 ---
-title: "Supplement 1A"
+title: "Supplement 1.B"
 author: "VKL"
@@
 library(scoringutils)
-library(viridis)
-
-library(ggeffects)
-library(emmeans)
-library(splines)
 
@@
 source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage
-### Estimate Relative WIS 
-pairWIS_fun <-function(x, df) {
-
-  df <-df %>%
-    pairwise_comparison(., summarise_by = c("model"),
-                        baseline = "COVIDhub-baseline") %>%
-    dplyr::select(model, scaled_rel_skill) %>%
-    distinct()
-}
-pairWIS_co_fun <-function(x, df) {
-
-  df <-df %>%
-    pairwise_comparison(., summarise_by = c("model", "pop_size_quant2"),
-                        baseline = "COVIDhub-baseline") %>%
-    dplyr::select(model, pop_size_quant2, scaled_rel_skill) %>%
-    distinct()
-}
 
@@
 axis.text_standard <-element_text(size=11)
-
-## Function for setting up legends in empty facet spaces
-library(gtable)
-library(cowplot)
-
-shift_legend <- function(p){
-
-  # check if p is a valid object
-  if(!"gtable" %in% class(p)){
-    if("ggplot" %in% class(p)){
-      gp <- ggplotGrob(p) # convert to grob
-    } else {
-      message("This is neither a ggplot object nor a grob generated from ggplotGrob. Returning original plot.")
-      return(p)
-    }
-  } else {
-    gp <- p
-  }
-
-  # check for unfilled facet panels
-  facet.panels <- grep("^panel", gp[["layout"]][["name"]])
-  empty.facet.panels <- sapply(facet.panels, function(i) "zeroGrob" %in% class(gp[["grobs"]][[i]]))
-  empty.facet.panels <- facet.panels[empty.facet.panels]
-  if(length(empty.facet.panels) == 0){
-    message("There are no unfilled facet panels to shift legend into. Returning original plot.")
-    return(p)
-  }
-
-  # establish extent of unfilled facet panels (including any axis cells in between)
-  empty.facet.panels <- gp[["layout"]][empty.facet.panels, ]
-  empty.facet.panels <- list(min(empty.facet.panels[["t"]]), min(empty.facet.panels[["l"]]),
-                             max(empty.facet.panels[["b"]]), max(empty.facet.panels[["r"]]))
-  names(empty.facet.panels) <- c("t", "l", "b", "r")
-
-  # extract legend & copy over to location of unfilled facet panels
-  guide.grob <- which(gp[["layout"]][["name"]] == "guide-box")
-  if(length(guide.grob) == 0){
-    message("There is no legend present. Returning original plot.")
-    return(p)
-  }
-  gp <- gtable_add_grob(x = gp,
-                        grobs = gp[["grobs"]][[guide.grob]],
-                        t = empty.facet.panels[["t"]],
-                        l = empty.facet.panels[["l"]],
-                        b = empty.facet.panels[["b"]],
-                        r = empty.facet.panels[["r"]],
-                        name = "new-guide-box")
-
-  # squash the original guide box's row / column (whichever applicable)
-  # & empty its cell
-  guide.grob <- gp[["layout"]][guide.grob, ]
-  if(guide.grob[["l"]] == guide.grob[["r"]]){
-    gp <- gtable_squash_cols(gp, cols = guide.grob[["l"]])
-  }
-  if(guide.grob[["t"]] == guide.grob[["b"]]){
-    gp <- gtable_squash_rows(gp, rows = guide.grob[["t"]])
-  }
-  gp <- gtable_remove_grobs(gp, "guide-box")
-
-  return(gp)
-}
 
@@
 
-```{r Fig S1A, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=11}
+```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=11}
 start_date <-as.Date('2020-07-28')
@@
 
-## Must have forecasts for at least 50 locations for states/territories/district and national
-include_locs <-function(x, df){
-
-  df <-df %>%
-    mutate(location=as.factor(location)) %>%
-    group_by(model, forecast_date) %>%
-    mutate(locs=length(unique(location))) %>% #[quantile==0.5 & target=="1 wk ahead inc case"]))) %>%
-    ungroup() %>%
-    filter(locs>=50)
-
-}
-
 ## Must have 75% of all counties per quantile per submission date forecasted
@@
     group_by(model, pop_size_quant2, sub_date) %>%
-    mutate(locs=length(unique(location))) %>% #[quantile==0.5 & target=="1 wk ahead inc case"]))) %>%
+    mutate(locs=length(unique(location))) %>% 
     ungroup() %>%
@@
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/updated_cases_nat_state_forecasts_2022-04-04.Rdata")
+```
 
-### National + state submissions
-nat_st <-all_dat %>%
+```{r Fig S1B, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=11}
+
+####
+load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_county_forecasts_2022-04-04.Rdata")
+size <-read.csv("C:/Users/oko8/Downloads/SVI2018_US_COUNTY.csv") %>%
+  dplyr::select(FIPS, E_TOTPOP) %>%
+  rename(location=FIPS) %>%
+  mutate(location=as.character(location),
+         location=ifelse(nchar(location)==4, paste0("0", location), location),
+         pop_size_quant2=cut(E_TOTPOP, breaks = quantile(E_TOTPOP, probs = seq(0, 1, 0.20)),
+                             include.lowest = TRUE, labels = 1:5)
+  ) %>% 
+  dplyr::select(-E_TOTPOP) 
+all_dat <-all_dat %>% left_join(., size, by="location") 
+rm(size)
+counts <-all_dat %>%
   filter(!(model %in% sec_models),
@@
 
-### National + state submissions that met inclusion criteria
-teams_nat_st <-all_dat %>%
+# Inclusion criteria for counties based on pop size
+all_dat <-all_dat %>%
   filter(!(model %in% sec_models),
-         sub_date >= start_date & sub_date <= stop_date) %>%
-  include_quant(df=.) %>% #all quantiles present
-  include_wks(df=.) %>% #all targets included 
-  include_locs(df=.) %>% #at least 50 locations
-  include_subs(df=.) %>% #submitted at least 50% of the time
+         sub_date <= stop_date) 
+all_dat <-all_dat %>% include_quant(df=.) 
+all_dat <-all_dat %>% include_wks(df=.) 
+all_dat <-all_dat %>% include_subs(df=.) 
+all_dat <-all_dat %>% include_locs_co(df=.)
+
+all_dat <-all_dat %>%
+  dplyr::select(-quants, -no_horizons, -locs, -locs_total, -percent_co, -total, -subs, -percent_sub) %>%
   dplyr::select(model) %>%
@@
 
-### Submission plots
-
-nat_st %>%
+counts %>%
   dplyr::select(-target, -target_end_date, -value) %>%
   distinct() %>%
-  group_by(sub_date, model) %>%
+  group_by(sub_date, model, pop_size_quant2) %>%
   summarize(locs=n()) %>%
+  rename_counts() %>%
   ungroup() %>%
   mutate(log_loc=log(locs)) %>%
+  mutate(total_sub=length(unique(sub_date))) %>%
   ungroup() %>%
-  mutate(total_sub=length(unique(sub_date))) %>%
-  group_by(model) %>%
+  group_by(model, pop_size_quant2) %>%
   mutate(wks_sub=length(sub_date),
@@
   ungroup() %>%
-  left_join(., teams_nat_st, by="model") %>%
+  left_join(., all_dat, by="model") %>%
   mutate(model_rename=ifelse(is.na(model_rename), model, model_rename),
@@
   ggplot(., aes(sub_date, model_rename)) +
-  geom_tile(aes(fill=log_loc)) +
-  scale_fill_gradient(low = "#c7e9c0", high = "#41ab5d") + 
-  geom_text(aes(label=locs), size=1.50) +
+  geom_tile(aes(fill=per_sub)) +
+  scale_fill_gradient(low = "#c7e9c0", high = "#4a1486",
+                      name="Percent of \nCounties \nForecasted") + 
   scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%B") +
+  facet_wrap(~ pop_size_quant2) +
   theme_bw() +
-  labs(title = "A. Primary Model* Submissions for National/State/Territory-Level Case Forecasts Over Time",
-       subtitle= "The number of locations forecasted per submission is labled",
+  labs(title = "B. Primary Model* Submissions for County-Level Case Forecasts Over Time",
        caption = "*Model met inclusion criteria") +
@@
         axis.title.y = element_blank(),
-        legend.position = "none")
+        strip.background = strip.background_standard, strip.text = strip.text_standard,
+        legend.position = "bottom")
 

### 2023-02-02 Code/Supplement 2_Outliers.Rmd
all code and figures

---
title: "Supplemtn 2: Team Specific GEEs & Exploration of Outlier Impact"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning=FALSE,message=FALSE)

library(tidyverse)
library(covidcast)
library(epiprocess)

library(geepack)
library(splines)

library(ggeffects)
library(emmeans)

library(gridExtra)
library(grid)
library(cowplot)

## Standardized formatting
strip.background_standard <-element_blank()
strip.text_standard <-element_text(size = 12, face='bold')
legend.text_standard <-element_text(size=12)
plot.caption_standard <-element_text(size=10, face = "italic")
axis.title.y_standard <-element_text(margin = margin(1, 10, 1, 1), size=12)
axis.text_standard <-element_text(size=11)

### Detection methods
detection_methods = bind_rows(
  tibble(method = "rm",
         args = list(list(detect_negatives = TRUE,
                          detection_multiplier = 2.5)),
         abbr = "rm"),
  tibble(method = "stl",
         args = list(list(detect_negatives = TRUE,
                          detection_multiplier = 2.5)),
         abbr = "stl_seasonal"),
  tibble(method = "stl",
         args = list(list(detect_negatives = TRUE,
                          detection_multiplier = 2.5,
                          seasonal_period = NULL)),
         abbr = "stl_nonseasonal"))

## Read in data and detect outliers
x <-covidcast_signal(data_source = "jhu-csse",
                      signal = "confirmed_incidence_num",
                      start_day =  "2020-07-26",
                      end_day = "2022-01-15",
                      geo_type = "state",
                      as_of = "2022-04-02") %>%
  dplyr::select(geo_value, time_value, cases=value) %>%   
  filter(geo_value!="as", geo_value!="gu", geo_value!="mp",
         geo_value!="pr", geo_value!="vi"#, geo_value!='dc'
         ) %>% 
  group_by(geo_value) %>%  
  mutate(outlier_info  = 
           detect_outlr(
             x = time_value, y = cases,
             methods = detection_methods,
             combiner = "median"))

## Subset to weeks with outliers
x_targets <-x %>% 
  unnest(outlier_info) %>%
  mutate(cases_corrected = combined_replacement) %>%
  mutate(flag_target=ifelse(cases!=cases_corrected, 1, 0)) %>%
  mutate(wk = as.Date(time_value, "%m/%d/%y"), 
         wk = as.Date(cut(wk,"week", start.on.monday = FALSE)) + 6) %>% 
  filter(flag_target==1) %>%
  dplyr::select(#cases_corrected, cases, 
    flag_target, geo_value, wk)

## rename locations based on state names
states <-read.csv("C:/Users/oko8/OneDrive - CDC/Projects/covid19-forecast-hub/data-locations/locations.csv") %>%
  rename(fips = location) %>%
  mutate(fips = as.character(fips)) %>%
  filter(nchar(fips)==2) %>%
  dplyr::select(abbreviation, location_name)

x_targets <-x_targets %>%
  rename(abbreviation=geo_value,
         date=wk) %>%
  mutate(abbreviation=toupper(abbreviation)) %>%
  left_join(., states, by="abbreviation") %>%
  distinct() %>%
  ungroup() %>%
  dplyr::select(-abbreviation) %>%
  mutate(location_name=as.factor(location_name))

x_submission <-x_targets %>%
  mutate(sub_date=date+3) %>%
  rename(flag_sub=flag_target) %>%
  dplyr::select(-date)

## Read in data
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_gee.Rdata")

WIS_rev <-WIS_gee %>%
   arrange(location_name, date) %>%
   left_join(., x_targets, by=c("location_name", "date")) %>%
   left_join(., x_submission, by=c("location_name", "sub_date")) %>%
   mutate(flag_target=ifelse(is.na(flag_target), 0, flag_target),
          flag_sub=ifelse(is.na(flag_sub), 0, flag_sub)) %>%
   group_by(model, location_name, target) %>%
   ungroup() %>%
   arrange(location_name, date) %>%
   filter(flag_target==0,#1,
          flag_sub==0)#1)

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

team <-c(as.character(unique(WIS_rev$model)))
dat_team_rev<-list()

model_rev <-list()

for(i in 1:length(team)){

  dat_team_rev[[i]] <-WIS_rev %>%
    filter(model==team[i]) %>%
    mutate(model=droplevels(model))

  model_rev[[i]] <-geeglm(formula =  WIS_log_std ~ ns(cases_log_std, df=2) + phase + target,
                      family = gaussian, data = dat_team_rev[[i]], id = location_name, wave=date,
                      corstr = "independence")  
}

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

team <-c(unique(as.character(WIS_rev$model))) 
dat_team_rev <-list()
means_sds <-list()
means_sds_phase <-list()

marg_means_int <-list()
marg_means <-list()

# Model Predictions 
for(i in 1:length(team)){

  dat_team_rev[[i]] <-as.data.frame(WIS_rev %>%
                                  filter(model==team[i]) %>%
                                  mutate(model=droplevels(model)) %>%
                                  ungroup())

  means_sds[[i]] <-dat_team_rev[[i]] %>%
    mutate(mean_log_WIS=mean(log(interval_score)),
           sd_log_WIS=sd(log(interval_score)),
           mean_log_cases=mean(log(true_value)),
           sd_log_cases=sd(log(true_value))
    ) %>%
    dplyr::select(model, contains("mean_"), contains("sd_")) %>%
    distinct()

  # Intercept
  marg_means_int[[i]] <-as.data.frame(emmeans(model_rev[[i]], ~1))
  marg_means_int[[i]] <-marg_means_int[[i]] %>%
    rename(predicted=emmean) %>%
    mutate(model=team[i],
           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_lo=(asymp.LCL*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_up=(asymp.UCL*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS) %>%
    mutate(predicted_back_rescale=exp(predicted_back),
           predicted_back_lo_rescale=exp(predicted_back_lo),
           predicted_back_up_rescale=exp(predicted_back_up))

  #Phases
  marg_means[[i]] <-ggemmeans(model_rev[[i]], terms=c("phase")) %>% #, "cases_log_std[-2:2]")) %>%
    rename(phase=x,
           cases=group) %>%

    mutate(model=team[i],
           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_lo=(conf.low*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_up=(conf.high*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS) %>%
    mutate(predicted_back_rescale=exp(predicted_back),
           predicted_back_lo_rescale=exp(predicted_back_lo),
           predicted_back_up_rescale=exp(predicted_back_up))

}
marg_means_int <-do.call(rbind.data.frame, marg_means_int)
marg_means <-do.call(rbind.data.frame, marg_means)

marg_means_int <-marg_means_int %>% 
  dplyr::select(-`1`) %>%
  mutate(model=as.factor(model),
         model=fct_reorder(model, predicted_back),
         phase="Mean across phases") 
levels <-levels(marg_means_int$model)

marg_means <-marg_means %>%

  ## Order by increasing error, on average
  mutate(model=as.factor(model),
         model=factor(model, levels = levels)) %>%
  mutate(phase=as.factor(ifelse(phase=="increasing", "Increasing",
                                    ifelse(phase=="decreasing", "Decreasing",
                                           ifelse(phase=="peak", "Peak",
                                                  ifelse(phase=="nadir", "Nadir", "Mean across phases"))))),
         phase=factor(phase, 
                          levels = c("Mean across phases", "Increasing", "Peak", "Decreasing",  "Nadir"))
  ) %>%
  ungroup()

baseline <-filter(marg_means_int, model=="COVIDhub-baseline")

# Figure
FigS2.3 <-marg_means_int %>%
  ggplot(.) +
  geom_point(aes(model, predicted_back_rescale)) +
  geom_linerange(aes(model, ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale)) +
  geom_hline(data=baseline, mapping=aes(yintercept=baseline$predicted_back_lo_rescale), color="red", linetype="dashed") + 
  geom_hline(data=baseline, mapping=aes(yintercept=baseline$predicted_back_up_rescale), color="red", linetype="dashed") +
  labs( y="Marginal Mean\n Weighted Interval Score", 
        title="A.") +
  theme_bw() +
  theme(axis.title.y=axis.title.y_standard, axis.text=axis.text_standard,
        legend.position = "bottom", legend.title = element_blank(), legend.text=legend.text_standard,
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1))

Fig6B <-marg_means %>%
  mutate(scaled_pred=predicted_back/baseline$predicted_back,
         SE_scaled=(predicted_back_up-predicted_back_lo)/3.92,
         prob_base=round(pnorm(baseline$predicted_back,
                               predicted_back, SE_scaled), 5),
         prob_label=ifelse(prob_base >=0.9, "*", NA),
         phase=fct_rev(phase)) %>%
  ggplot(.) +
  geom_tile(aes(model, phase, fill=scaled_pred)) +
  geom_text(aes(model, phase, label=prob_label), size=4) +
  scale_fill_gradient2(low = "#7fcdbb", high = "#fecc5c", midpoint = 1.0,
                       name="Marginal mean Weighted Interval Score  \nscaled to the marginal mean  \nof COVIDhub-baseline model  \nacross all phases",
                       guide = guide_colourbar(barheight = 1.5)) +
  labs(y="", title="B.",
       caption="*Probability >= 0.90 that forecasts outperform baseline") + 
  theme_bw() +
  theme(legend.position = "bottom", legend.title.align=0.5, legend.box.just = "center", 
    plot.caption = plot.caption_standard,
    strip.text=strip.text_standard, strip.background=strip.background_standard,
    panel.border = element_rect(colour = "black", fill = NA),
    axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1), axis.text=axis.text_standard,
    axis.ticks.y=element_blank())

```

```{r Fig S2.3, echo=FALSE, warning=F, message=F, fig.height=8.5, fig.width=8.5}

FigS2.3_updated <-FigS2.3 + theme(axis.text.x = element_blank())

plot_grid(FigS2.3_updated, Fig6B, rel_heights  = c(0.5, 1), axis = "l",
          align="v", nrow = 2)

```

### 2023-02-02 Code/Supplement 2_Revisions.Rmd
all code and figures

---
title: "Supplement 2: Team Specific GEEs  & Exploration of Revision Impact"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning=FALSE,message=FALSE)

library(tidyverse)
library(covidcast)
library(epiprocess)

library(geepack)
library(splines)

library(ggeffects)
library(emmeans)

library(gridExtra)
library(grid)
library(cowplot)

## Standardized formatting
strip.background_standard <-element_blank()
strip.text_standard <-element_text(size = 12, face='bold')
legend.text_standard <-element_text(size=12)
plot.caption_standard <-element_text(size=10, face = "italic")
axis.title.y_standard <-element_text(margin = margin(1, 10, 1, 1), size=12)
axis.text_standard <-element_text(size=11)

## Read in data used in analysis
main_dat <-covidcast_signal(data_source = "jhu-csse",
                      signal = "confirmed_incidence_num",
                      start_day = "2020-07-26",
                      end_day = "2022-01-15",
                      geo_type = "state",
                      as_of = "2022-04-02") %>%
  dplyr::select(geo_value, time_value, cases_now=value) %>%   
  filter(geo_value!="as", geo_value!="gu", geo_value!="mp",
         geo_value!="pr", geo_value!="vi"#, geo_value!='dc'
         ) %>% 
  group_by(geo_value)

dates <-seq.Date(as.Date("2020-08-01"), as.Date("2022-01-15"), by="week")
hx_dat <-list()
for(i in 1:length(dates)){
  hx_dat[[i]] <-covidcast_signal(data_source = "jhu-csse",
                      signal = "confirmed_incidence_num",
                      start_day =dates[[i]] - 6,
                      end_day = dates[[i]], 
                      geo_type = "state",
                      as_of = dates[[i]] +1) %>%
  dplyr::select(geo_value, time_value, cases_last=value) %>%   
  filter(geo_value!="as", geo_value!="gu", geo_value!="mp",
         geo_value!="pr", geo_value!="vi"#, geo_value!='dc'
         ) %>% 
  mutate(wk = as.Date(time_value, "%m/%d/%y"), 
         wk = as.Date(cut(wk,"week", start.on.monday = FALSE)) + 6)  
}
hx_dats_all <-do.call(rbind, hx_dat)

cases_all <-main_dat %>%
  left_join(., hx_dats_all, by=c("geo_value", "time_value")) %>%
  mutate(revision=ifelse(cases_now==cases_last, 0, 1)) %>%
  filter(revision==1) %>%
  dplyr::select(geo_value, wk, revision) %>%
  distinct()

## rename locations based on state names
states <-read.csv("C:/Users/oko8/OneDrive - CDC/Projects/covid19-forecast-hub/data-locations/locations.csv") %>%
  rename(fips = location) %>%
  mutate(fips = as.character(fips)) %>%
  filter(nchar(fips)==2) %>%
  dplyr::select(abbreviation, location_name)

cases_all <-cases_all %>%
  rename(abbreviation=geo_value,
         date=wk) %>%
  mutate(abbreviation=toupper(abbreviation)) %>%
  left_join(., states, by="abbreviation") %>%
  distinct() %>%
  ungroup() %>%
  dplyr::select(-abbreviation) %>%
  mutate(location_name=as.factor(location_name))

## Read in data
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_gee.Rdata")

WIS_rev <-WIS_gee %>%
   arrange(location_name, date) %>%
   left_join(., cases_all, by=c("location_name", "date")) %>%
   mutate(revision=ifelse(is.na(revision), 0, revision)) %>%
   group_by(model, location_name, target) %>%
   ungroup() %>%
   arrange(location_name, date) %>%
   filter(revision==0) %>%
   mutate(location_name=droplevels(location_name))

```

```{r Fig S2.1, echo=FALSE, warning=FALSE, message=FALSE, fig.height=12, fig.width=20}

main_dat <-main_dat %>%
  mutate(geo_value=toupper(geo_value)) %>%
  left_join(., states, by=c("geo_value"="abbreviation"))

hx_dats_all %>%
  mutate(geo_value=toupper(geo_value)) %>%
  left_join(., states, by=c("geo_value"="abbreviation")) %>%
  ungroup() %>%
  ggplot(.) +
  geom_line(aes(time_value, cases_last), color="#cb181d", alpha=0.55) + #as.factor(wk)),  alpha=0.65) +
  geom_line(main_dat, mapping=aes(time_value, cases_now), size=0.65) +
  facet_wrap(~ geo_value, scales="free_y") +
  scale_x_date(date_labels="%b-%y", breaks = hx_dats_all$wk, date_breaks ="3 months", date_minor_breaks ="1 month") +
  labs(y="Reported cases") +
  theme_bw() +
  theme(legend.position = "none", 
        axis.title.x=element_blank(), axis.text.x=element_text(size=6),
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        panel.border = element_rect(colour = "black", fill = NA))

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

team <-c(as.character(unique(WIS_rev$model)))
dat_team_rev<-list()

model_rev <-list()

for(i in 1:length(team)){

  dat_team_rev[[i]] <-WIS_rev %>%
    filter(model==team[i]) %>%
    mutate(model=droplevels(model))

  model_rev[[i]] <-geeglm(formula =  WIS_log_std ~ ns(cases_log_std, df=2) + phase + target,
                      family = gaussian, data = dat_team_rev[[i]], id = location_name, wave=date,
                      corstr = "independence")  
}

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

team <-c(unique(as.character(WIS_rev$model))) 
dat_team_rev <-list()
means_sds <-list()

marg_means_int <-list()
marg_means <-list()

# Model Predictions 
for(i in 1:length(team)){

  dat_team_rev[[i]] <-as.data.frame(WIS_rev %>%
                                  filter(model==team[i]) %>%
                                  mutate(model=droplevels(model)) %>%
                                  ungroup())

  means_sds[[i]] <-dat_team_rev[[i]] %>%
    mutate(mean_log_WIS=mean(log(interval_score)),
           sd_log_WIS=sd(log(interval_score)),
           mean_log_cases=mean(log(true_value)),
           sd_log_cases=sd(log(true_value))
    ) %>%
    dplyr::select(model, contains("mean_"), contains("sd_")) %>%
    distinct()

  # Intercept
  marg_means_int[[i]] <-as.data.frame(emmeans(model_rev[[i]], ~1))
  marg_means_int[[i]] <-marg_means_int[[i]] %>%
    rename(predicted=emmean) %>%
    mutate(model=team[i],
           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_lo=(asymp.LCL*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_up=(asymp.UCL*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS) %>%
    mutate(predicted_back_rescale=exp(predicted_back),
           predicted_back_lo_rescale=exp(predicted_back_lo),
           predicted_back_up_rescale=exp(predicted_back_up))

  #Phases
  marg_means[[i]] <-ggemmeans(model_rev[[i]], terms=c("phase")) %>% #, "cases_log_std[-2:2]")) %>%
    rename(phase=x,
           cases=group) %>%

    mutate(model=team[i],
           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_lo=(conf.low*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_up=(conf.high*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS) %>%
    mutate(predicted_back_rescale=exp(predicted_back),
           predicted_back_lo_rescale=exp(predicted_back_lo),
           predicted_back_up_rescale=exp(predicted_back_up)) 
}
marg_means_int <-do.call(rbind.data.frame, marg_means_int)
marg_means <-do.call(rbind.data.frame, marg_means)

marg_means_int <-marg_means_int %>% 
  dplyr::select(-`1`) %>%
  mutate(model=as.factor(model),
         model=fct_reorder(model, predicted_back),
         phase="Mean across phases") 
levels <-levels(marg_means_int$model)

marg_means <-marg_means %>%

  ## Order by increasing error, on average
  mutate(model=as.factor(model),
         model=factor(model, levels = levels)) %>%
  mutate(phase=as.factor(ifelse(phase=="increasing", "Increasing",
                                    ifelse(phase=="decreasing", "Decreasing",
                                           ifelse(phase=="peak", "Peak",
                                                  ifelse(phase=="nadir", "Nadir", "Mean across phases"))))),
         phase=factor(phase, 
                          levels = c("Mean across phases", "Increasing", "Peak", "Decreasing",  "Nadir"))
  ) %>%
  ungroup()

baseline <-filter(marg_means_int, model=="COVIDhub-baseline")

# Figure
FigS2.2 <-marg_means_int %>%
  ggplot(.) +
  geom_point(aes(model, predicted_back_rescale)) +
  geom_linerange(aes(model, ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale)) +
  geom_hline(data=baseline, mapping=aes(yintercept=baseline$predicted_back_lo_rescale), color="red", linetype="dashed") + 
  geom_hline(data=baseline, mapping=aes(yintercept=baseline$predicted_back_up_rescale), color="red", linetype="dashed") +
  labs( y="Marginal Mean\n Weighted Interval Score", 
        title="A.") +
  theme_bw() +
  theme(axis.title.y=axis.title.y_standard, axis.text=axis.text_standard,
        legend.position = "bottom", legend.title = element_blank(), legend.text=legend.text_standard,
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust=1))

Fig6B <-marg_means %>%
  mutate(scaled_pred=predicted_back/baseline$predicted_back,
         SE_scaled=(predicted_back_up-predicted_back_lo)/3.92,
         prob_base=round(pnorm(baseline$predicted_back,
                               predicted_back, SE_scaled), 5),
         prob_label=ifelse(prob_base >=0.9, "*", NA),
         phase=fct_rev(phase)) %>%
  ggplot(.) +
  geom_tile(aes(model, phase, fill=scaled_pred)) +
  geom_text(aes(model, phase, label=prob_label), size=4) +
  scale_fill_gradient2(low = "#7fcdbb", high = "#fecc5c", midpoint = 1.0,
                       name="Marginal mean Weighted Interval Score  \nscaled to the marginal mean  \nof COVIDhub-baseline model  \nacross all phases",
                       guide = guide_colourbar(barheight = 1.5)) +
  labs(y="", title="B.",
       caption="*Probability >= 0.90 that forecasts outperform baseline") + 
  theme_bw() +
  theme(#axis.title.y=axis.title.y_standard,
    legend.position = "bottom", legend.title.align=0.5, legend.box.just = "center", 
    plot.caption = plot.caption_standard,
    strip.text=strip.text_standard, strip.background=strip.background_standard,
    panel.border = element_rect(colour = "black", fill = NA),
    axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1), axis.text=axis.text_standard,
    axis.ticks.y=element_blank())#, axis.text.y=element_blank())

```

```{r Fig S2.2, echo=FALSE, warning=F, message=F, fig.height=8.5, fig.width=8.5}

FigS2.2_updated <-FigS2.2 + theme(axis.text.x = element_blank())

plot_grid(FigS2.2_updated, Fig6B, rel_heights  = c(0.5, 1), axis = "l",
          align="v", nrow = 2)

```

### 2023-02-02 Code/Supplement 3.1_figure.rmd
all code and figures

---
title: "Supplement 3.1"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning=FALSE,message=FALSE)

library(tidyverse)
library(tidytext)
library(ggrepel)

library(gridExtra)
library(cowplot)
library(scoringutils)
library(viridis)

library(ggeffects)
library(emmeans)
library(splines)

setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")

### Need functions
source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage

## Standardized formatting
strip.background_standard <-element_blank()
strip.text_standard <-element_text(size=10, face='bold')
legend.text_standard <-element_text(size=12)
plot.caption_standard <-element_text(size=11, face = "italic")
axis.title.y_standard <-element_text(margin = margin(1, 10, 1, 1), size=12)
axis.text_standard <-element_text(size=11)

## Change labels for counties
 rename_counts <-function(df) {   
   df <-df %>%
     mutate(pop_size_quant2=ifelse(pop_size_quant2==1, "County Forecasts: Size Quantile 1",
                                 ifelse(pop_size_quant2==2, "County Forecasts: Size Quantile 2",
                                        ifelse(pop_size_quant2==3, "County Forecasts: Size Quantile 3", 
                                               ifelse(pop_size_quant2==4, "County Forecasts: Size Quantile 4", "County forecasts: Size Quantile 5")))))
}

 stop_date <-as.Date("2021-12-21")
 cut_date <-as.Date("2021-12-21")
```

## Supplemental Figures

### Supplement 3: Non large country figures

#### Figure 1. Mean WIS and Mean 95% Coverage

```{r fig s3.1, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=20}

## WIS estimates

mean_WIS <-function() {
  ## Large counties
  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.rdata")

  WIS_counties <-WIS_all %>%
    filter(type=="quantile") %>%
    summarise_scores(by = c("model"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill) %>%
    distinct() %>%
    mutate(pop_size_quant2="County Forecasts: Size Quantile 5",
           model_reorder=fct_reorder(model, scaled_rel_skill))
  levels_model <-levels(WIS_counties$model_reorder)

  ## Non Large counties
  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_non large counties_all subs.rdata")

  WIS_counties_other <-WIS_all %>%
    filter(type=="quantile") %>%
    summarise_scores(by = c("model", "pop_size_quant2"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill, pop_size_quant2) %>%
    distinct() %>%
    rename_counts() %>%
    add_row(model="FRBSF_Wilson-Econometric", pop_size_quant2="County Forecasts: Size Quantile 1") %>% #,
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 1") %>% #, 
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 2") %>% #, 
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 3") %>% #, 
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 4") %>% 
    mutate(model_reorder=model) %>%
    mutate(model_reorder=factor(model, levels_model))

  mean_WIS <-WIS_counties %>%
    bind_rows(., WIS_counties_other) %>%
    mutate(key=pop_size_quant2) %>%
    mutate(value_display=format(round(scaled_rel_skill, digits=2), nsmall = 2),
           value_display=ifelse(value_display=="  NA", NA, value_display))

  }
mean_WIS <-mean_WIS() 
mean_WIS$model_reorder <-fct_rev(mean_WIS$model_reorder)
levels_model <-levels(mean_WIS$model_reorder)

WIS.heatmap <-mean_WIS %>%
  ungroup() %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=scaled_rel_skill)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 1.0, na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="Relative Weighted Interval Score") +
  theme(axis.title.x = element_blank(), axis.text.y=element_blank(),
        axis.title.y = element_blank(), axis.text=axis.text_standard,
        legend.position="bottom")

############################################################################
############################################################################

### Coverage estimates

cov.95 <-function() {
  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")

  ## Large counties
  coverage_counties <- dat_large_count %>%
    filter(sub_date <= cut_date) %>%
    coverage(df=.) %>%
    group_by(model) %>%
    summarize(mean_count=mean(coverage.95)) %>%
    mutate(pop_size_quant2="County Forecasts: Size Quantile 5")

  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")

  ## Non Large counties
  coverage_counties_other <- dat_other_count %>%
    coverage(df=.) %>%
    group_by(model, pop_size_quant2) %>%
    summarize(mean_count=mean(coverage.95)) %>%
    ungroup()

  cov.95 <-coverage_counties %>%
    bind_rows(., coverage_counties_other) %>%
    mutate(value_display=format(round(mean_count, digits=2), nsmall = 2),
           value_display=ifelse(value_display=="  NA", NA, value_display))
}
cov.95 <-cov.95() %>%
  rename_counts() %>%
  ungroup() %>%
  mutate(key=pop_size_quant2) %>%
  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quantile 1") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 1") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 2") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 3") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 4") %>%
  mutate(model_reorder=factor(model, levels_model))

cov.heatmap <-cov.95 %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=mean_count)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient2(low = "white", mid = "#f7fcb9", high = "#31a354", midpoint = 0.75, na.value = "grey75") +
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="95% Coverage") +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), axis.text.y=element_blank(),
        axis.text=axis.text_standard,
        legend.position="bottom")

############################################################################
############################################################################

### Submissions over time

submissions <-function(df) {

  start_date <-as.Date("2020-07-28")
  stop_date <-as.Date("2021-12-21")

  df <-df %>%
    filter(sub_date >= start_date & sub_date <= stop_date) %>% 
    dplyr::select(forecast_date, model, location, target, sub_date, pop_size_quant2) %>%
    distinct() %>%
    dplyr::select(-target) %>%
    distinct() %>%
    group_by(sub_date, model, pop_size_quant2) %>%
    summarize(locs=n()) %>%
    ungroup() %>%
    mutate(total_sub=length(unique(sub_date))) %>%
    group_by(model, pop_size_quant2) %>%
    mutate(wks_sub=length(sub_date),
           per_sub=(wks_sub/total_sub)) %>%
    ungroup() %>%
  dplyr::select(-locs, -sub_date) %>%
  distinct()

  return(df)

}

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
subs_co <-submissions(df=dat_large_count) %>%
  mutate(pop_size_quant2="County Forecasts: Size Quantile 5")

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")
subs_co_other <-submissions(df=dat_other_count) %>%
  rename_counts()

all_subs <-subs_co %>%
  bind_rows(., subs_co_other) %>%
  mutate(key=pop_size_quant2,
         value_display=format(round(per_sub, digits=2), nsmall = 2),
         value_display=ifelse(value_display=="  NA", NA, value_display)) %>%
  ungroup() %>%
  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quantile 1") %>%  
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 1") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 2") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 3") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 4") %>%
  mutate(model_reorder=factor(model, levels_model)) %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=per_sub)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient(low = "#fde0dd", high = "#c51b8a", na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="% Weeks \nSubmitted") +
  theme(axis.title.x = element_blank(),   
        axis.title.y = element_blank(), 
        axis.text=axis.text_standard,
        legend.position="bottom")

############################################################################
############################################################################

plot_grid(all_subs, WIS.heatmap, cov.heatmap,
          rel_widths = c(0.95, 0.70, 0.66),
          nrow=1)

```

### 2023-02-02 Code/Supplement 3.2 and 3.3_figures.rmd
all code and figures

---
title: "Supplement 3.2 and 3.3"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning=FALSE,message=FALSE)

library(tidyverse)
library(tidytext)
library(ggrepel)

library(gridExtra)
library(cowplot)
library(scoringutils)
library(viridis)

library(ggeffects)
library(emmeans)
library(splines)

setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")

### Need functions
source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage

## Standardized formatting
strip.background_standard <-element_blank()
strip.text_standard <-element_text(size=10, face='bold')
legend.text_standard <-element_text(size=12)
plot.caption_standard <-element_text(size=11, face = "italic")
axis.title.y_standard <-element_text(margin = margin(1, 10, 1, 1), size=12)
axis.text_standard <-element_text(size=11)

## Change labels for counties
 rename_counts <-function(df) {   
   df <-df %>%
     mutate(pop_size_quant2=ifelse(pop_size_quant2==1, "County Forecasts: Size Quantile 1",
                                 ifelse(pop_size_quant2==2, "County Forecasts: Size Quantile 2",
                                        ifelse(pop_size_quant2==3, "County Forecasts: Size Quantile 3", 
                                               ifelse(pop_size_quant2==4, "County Forecasts: Size Quantile 4", "County forecasts: Size Quantile 5")))))
}

 stop_date <-as.Date("2021-12-21")
```

## Supplemental Figures

### Supplement 3: Non large country figures

#### Absolute WIS

```{r Fig S3.3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=11, fig.width=12}

# Function for WIS over time
WIS.ot.fig_dat <-function(df) {

  sub_date <-c(unique(df$sub_date))
  model <-c(as.character(unique(df$model)))
  model_dates <-crossing(sub_date, model)

  cast_dates <-df %>%
    dplyr::select(sub_date, date, pop_size_quant2) %>%
    distinct() %>%
    left_join(model_dates, by="sub_date")

  dat <-df %>%
    full_join(cast_dates, ., by=c("model", "sub_date", "date", "pop_size_quant2")) %>%
    mutate(bold=ifelse(model=="COVIDhub-baseline" | model=="COVIDhub-4_week_ensemble", "T", "F")) %>%
    group_by(model, date, bold, pop_size_quant2) %>%
    summarize(abWIS=mean(interval_score, na.rm=TRUE)) %>%
    ungroup() %>%
    mutate(grouping=ifelse(model=="COVIDhub-baseline", "COVIDhub-baseline", 
                           ifelse(model=="COVIDhub-4_week_ensemble", "COVIDhub-4_week_ensemble", "Other teams"))) #%>%
  return(dat)

}
cov.ot.fig_dat <-function(df) {

  sub_date <-c(unique(df$sub_date))
  model <-c(as.character(unique(df$model)))
  model_dates <-crossing(sub_date, model)

  cov <-df %>%
    group_by(model, target_end_date, pop_size_quant2) %>%
    coverage(df=.) %>%
    summarize(cov.95=mean(coverage.95))

  dat <-df %>%
    dplyr::select(sub_date, target_end_date, pop_size_quant2) %>%
    distinct() %>%
    left_join(., model_dates, by=c("sub_date")) %>%
    dplyr::select(-sub_date) %>%
    left_join(., cov, by=c("model", "target_end_date", "pop_size_quant2")) %>%
    distinct() %>%
    ungroup() %>%
    mutate(grouping=ifelse(model=="COVIDhub-baseline", "COVIDhub-baseline", 
                           ifelse(model=="COVIDhub-4_week_ensemble", "COVIDhub-4_week_ensemble", "Other teams"))) %>%
    mutate(bold=ifelse(model=="COVIDhub-baseline" | model=="COVIDhub-4_week_ensemble", "T", "F"))

  return(dat)

}
ot.plot <-function(df, x, y) {

  ggplot() +
    geom_line(data=filter(df, bold=="F"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    geom_point(data=filter(df, bold=="F"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    geom_line(data=filter(df, bold=="T"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    geom_point(data=filter(df, bold=="T"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    scale_size_manual(values = c("T"=1.25, "F"=0.85)) +
    scale_x_date(date_labels="%b-%y", breaks = df$x, date_breaks ="3 months", date_minor_breaks ="1 month") +
    geom_vline(xintercept = as.numeric(stop_date), linetype=4, size=1.05) +
    scale_colour_manual(name="",
                        values = c("COVIDhub-baseline"="#762a83",
                                   "COVIDhub-4_week_ensemble"="#1b7837",
                                   "Other teams"="grey80"),
                        labels=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week_ensemble"),
                        breaks=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week_ensemble")) +
    guides(size = "none") + 
    theme_bw() +
    theme(legend.position = "none", 
          axis.title.x = element_blank())
}

###########################################################################
############################################################################

### WIS Over time
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_non large counties_all subs.rdata")

## National
WIS_ot <-WIS.ot.fig_dat(WIS_all) %>%
  rename_counts() #%>%
  #mutate(abWIS=ifelse(abWIS=="NaN", NA, abWIS))
WIS <-ot.plot(WIS_ot, date, abWIS)  +
  facet_wrap(~ pop_size_quant2, ncol = 1) +
  scale_y_continuous(trans='log10') +
  theme(axis.title.x=element_blank(),
        legend.position = c(0.25, 0.94),legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.025,0.025,0.025,0.025)),
        legend.key = element_rect(colour = NA, fill = NA), 
        strip.background = strip.background_standard, strip.text = strip.text_standard) +
  labs(title="A. Average Weighted Interval Score for County Forecasts",
       x = "Forecast target date",
       y = "Average Weighted Interval Score")

############################################################################
############################################################################

### Coverage Over time
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")

cov_ot <-cov.ot.fig_dat(dat_other_count) %>%
  rename_counts() 
cov <-ot.plot(cov_ot, target_end_date, cov.95)  +
  geom_hline(yintercept = 0.95,  linetype=6, size=1.05) +
  facet_wrap(~ pop_size_quant2, ncol = 1) +
  #theme(axis.title.x=element_blank()) +  
  labs(title="B. 95% Coverage for County Forecasts",
       x = "Forecast target date",
       y = "95% Coverage") + 
  theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5),
        strip.background = strip.background_standard, strip.text = strip.text_standard)

############################################################################
############################################################################

grid.arrange(WIS, cov,
             ncol=2)

```

####  Coverage.

```{r Fig S3.2, echo=FALSE, warning=F, message=F, fig.height=8.5, fig.width=9}

# Read in and manipulate data + plot structure
cov.fig_dat <-function(df) {
  coverage <-df %>%
    coverage(df=.) %>%
    group_by(model, pop_size_quant2) %>%
    summarize(coverage.95=mean(coverage.95),
              coverage.80=mean(coverage.80),
              coverage.50=mean(coverage.50)) %>%
    gather("expected_cov", "observed_cov", coverage.95:coverage.50) %>%
    mutate(expected_cov=gsub("coverage.", "", expected_cov),
           expected_cov=as.numeric(expected_cov),
           expected_cov=expected_cov/100,
           bold=ifelse(model=="COVIDhub-baseline" | model=="COVIDhub-4_week_ensemble", "T", "F"),
          grouping=ifelse(model=="COVIDhub-baseline", "COVIDhub-baseline", 
                           ifelse(model=="COVIDhub-4_week_ensemble", "COVIDhub-4_week_ensemble", "Other teams")))
  return(coverage)
}
data_labels <-function(df) {

  ensemble_cov <-df%>%
    filter(model=="COVIDhub-4_week_ensemble")

  data_labels <-df %>%  
    filter(model!="COVIDhub-4_week_ensemble") %>%
    mutate(test_95=ifelse(expected_cov==0.95 & observed_cov > ensemble_cov$observed_cov[ensemble_cov$expected_cov==0.95], 1, NA),
           test_80=ifelse(expected_cov==0.80 & observed_cov > ensemble_cov$observed_cov[ensemble_cov$expected_cov==0.80], 1, NA),
           test_50=ifelse(expected_cov==0.50 & observed_cov > ensemble_cov$observed_cov[ensemble_cov$expected_cov==0.50], 1, NA)) %>%
    filter(!is.na(test_95) | !is.na(test_80) | !is.na(test_50)) %>%
    group_by(model) %>%
    mutate(model_count=n()) %>%
    filter(model_count==3 & expected_cov==0.95) %>%
    mutate(model=ifelse(model=="JHU_UNC_GAS-StatMechPool", "JHU_UNC_GAS\n-StatMechPool", model)) %>%
    mutate(model=ifelse(model=="MOBS-GLEAM_COVID", "MOBS-GLEAM_\nCOVID", model)) %>%
    mutate(model=ifelse(model=="IEM_MED-CovidProject", "IEM_MED\n-CovidProject", model)) %>%
    mutate(model=ifelse(model=="COVIDhub-trained_ensemble", "COVIDhub\n-trained\n_ensemble", model)) %>%
  return(data_labels)
  }
cov.plot <-function(df, df2) {
  ggplot(df) +
    geom_line(data=filter(df, bold=="F"), 
              mapping=aes(expected_cov, observed_cov, group=model, color=grouping, size=bold, alpha=0.75)) +
    geom_point(data=filter(df, bold=="F"), 
               mapping=aes(expected_cov, observed_cov, group=model, color=grouping), size=1.5) +
    geom_line(data=filter(df, bold=="T"), 
              mapping=aes(expected_cov, observed_cov, group=model, color=grouping, size=bold, alpha=0.75)) +
    geom_point(data=filter(df, bold=="T"), 
               mapping=aes(expected_cov, observed_cov, group=model, color=grouping), size=3) +
    geom_line(aes(expected_cov, expected_cov, color=grouping, group=model), linetype="dashed", size=1.5, color="black") +
    scale_size_manual(values = c("T"=1.5, "F"=0.85)) +
    scale_colour_manual(values = c("COVIDhub-baseline"="#762a83",
                                   "COVIDhub-4_week_ensemble"="#1b7837",
                                   "Other teams"="grey70"),
                        labels=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week\n_ensemble"),
                        breaks=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week_ensemble")) +
    guides(size = "none", alpha="none") +
    labs(y="Observed Coverage") +
    theme_bw()  + 
    theme(legend.position = "none", 
          axis.title.x = element_blank()) +
    geom_text_repel(data=df2,
                    mapping=aes(expected_cov, observed_cov, label=model), size=3,
                    force=1, point.padding=unit(0.5,'lines'), nudge_x =0.1,
                    segment.size= 0.05,  segment.color="grey50",
                    direction="y", #hjust = "right",
                    vjust=0.5) +
    scale_x_continuous(expand = expansion(mult = c(0.05, 0.25)))
}

# Figures

# All Counties
coverage_count1 <-cov.fig_dat(filter(dat_other_count, pop_size_quant2==1, sub_date <= stop_date))
labels_count1 <-data_labels(coverage_count1)

p1 <-cov.plot(coverage_count1, labels_count1) +
  labs(title="County Forecasts: Size Quantile 1") +
  theme(legend.position = c(0.02, 0.88), legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.5,1,1,1)),
        legend.key = element_rect(colour = NA, fill = NA))

coverage_count2 <-cov.fig_dat(filter(dat_other_count, pop_size_quant2==2, sub_date <= stop_date))
labels_count2 <-data_labels(coverage_count2) 
p2 <-cov.plot(coverage_count2, labels_count2) +
  labs(title="County Forecasts: Size Quantile 2", 
       y="")

coverage_count3 <-cov.fig_dat(filter(dat_other_count, pop_size_quant2==3, sub_date <= stop_date))
labels_count3 <-data_labels(coverage_count3) 
p3 <-cov.plot(coverage_count3, labels_count3) +
  labs(title="County Forecasts: Size Quantile 3",
       x="Expected Coverage")

coverage_count4 <-cov.fig_dat(filter(dat_other_count, pop_size_quant2==4, sub_date <= stop_date))
labels_count4 <-data_labels(coverage_count4) 
p4 <-cov.plot(coverage_count4, labels_count4) +
  labs(title="County Forecasts: Size Quantile 4",
       y="",
       x="Expected Coverage")

grid.arrange(p1, p2, p3, p4,
              ncol=2)

```

### 2023-02-02 Code/Supplement 5_all figures.Rmd
all code and figures

---
title: "Supplement 5"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning=FALSE,message=FALSE)

library(tidyverse)
library(tidytext)
library(ggrepel)

library(gridExtra)
library(cowplot)
library(ggpubr)
library(scoringutils)
library(viridis)

library(ggeffects)
library(emmeans)
library(splines)

setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")

### Need functions
source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage

## Standardized formatting
strip.background_standard <-element_blank()
strip.text_standard <-element_text(size=10, face='bold')
legend.text_standard <-element_text(size=12)
plot.caption_standard <-element_text(size=11, face = "italic")
axis.title.y_standard <-element_text(margin = margin(1, 10, 1, 1), size=12)
axis.text_standard <-element_text(size=11)

 stop_date <-as.Date("2021-12-21")
 cut_date <-as.Date("2021-12-21")

```

## Supplemental Figures

### Supplement 5: Horizon specific plots

####  Coverage.

```{r, echo=FALSE, warning=F, message=F, fig.show='hide'}

# Read in and manipulate data + plot structure
cov.fig_dat <-function(df) {
  coverage <-df %>%
    coverage(df=.) %>%
    group_by(model, target) %>%
    summarize(coverage.95=mean(coverage.95),
              coverage.80=mean(coverage.80),
              coverage.50=mean(coverage.50)) %>%
    gather("expected_cov", "observed_cov", coverage.95:coverage.50) %>%
    mutate(expected_cov=gsub("coverage.", "", expected_cov),
           expected_cov=as.numeric(expected_cov),
           expected_cov=expected_cov/100,
           bold=ifelse(model=="COVIDhub-baseline" | model=="COVIDhub-4_week_ensemble", "T", "F"),
          grouping=ifelse(model=="COVIDhub-baseline", "COVIDhub-baseline", 
                           ifelse(model=="COVIDhub-4_week_ensemble", "COVIDhub-4_week_ensemble", "Other teams")))
  return(coverage)
}
data_labels <-function(df) {

  ensemble_cov1 <-df %>%
    filter(model=="COVIDhub-4_week_ensemble",
           grepl("1",target))

  ensemble_cov4 <-df %>%
    filter(model=="COVIDhub-4_week_ensemble",
           grepl("4",target))

  data_labels1 <-df %>%  
    filter(model!="COVIDhub-4_week_ensemble",
           grepl("1",target)) %>%
    mutate(test_95=ifelse(expected_cov==0.95 & observed_cov > ensemble_cov1$observed_cov[ensemble_cov1$expected_cov==0.95], 1, NA),
           test_80=ifelse(expected_cov==0.80 & observed_cov > ensemble_cov1$observed_cov[ensemble_cov1$expected_cov==0.80], 1, NA),
           test_50=ifelse(expected_cov==0.50 & observed_cov > ensemble_cov1$observed_cov[ensemble_cov1$expected_cov==0.50], 1, NA)) %>%
    filter(!is.na(test_95) | !is.na(test_80) | !is.na(test_50)) %>%
    group_by(model) %>%
    mutate(model_count=n()) %>%
    filter(model_count==3 & expected_cov==0.95) %>%
    mutate(model=ifelse(model=="JHU_UNC_GAS-StatMechPool", "JHU_UNC_GAS\n-StatMechPool", model)) %>%
    #mutate(model=ifelse(model=="MOBS-GLEAM_COVID", "MOBS-GLEAM_\nCOVID", model)) %>%
    mutate(model=ifelse(model=="IEM_MED-CovidProject", "IEM_MED\n-CovidProject", model)) %>%
    mutate(model=ifelse(model=="COVIDhub-trained_ensemble", "COVIDhub\n-trained\n_ensemble", model))

  data_labels4 <-df %>%  
    filter(model!="COVIDhub-4_week_ensemble",
           grepl("4",target)) %>%
    mutate(test_95=ifelse(expected_cov==0.95 & observed_cov > ensemble_cov4$observed_cov[ensemble_cov4$expected_cov==0.95], 1, NA),
           test_80=ifelse(expected_cov==0.80 & observed_cov > ensemble_cov4$observed_cov[ensemble_cov4$expected_cov==0.80], 1, NA),
           test_50=ifelse(expected_cov==0.50 & observed_cov > ensemble_cov4$observed_cov[ensemble_cov4$expected_cov==0.50], 1, NA)) %>%
    filter(!is.na(test_95) | !is.na(test_80) | !is.na(test_50)) %>%
    group_by(model) %>%
    mutate(model_count=n()) %>%
    filter(model_count==3 & expected_cov==0.95) %>%
    mutate(model=ifelse(model=="JHU_UNC_GAS-StatMechPool", "JHU_UNC_GAS\n-StatMechPool", model)) %>%
    #mutate(model=ifelse(model=="MOBS-GLEAM_COVID", "MOBS-GLEAM_\nCOVID", model)) %>%
    mutate(model=ifelse(model=="IEM_MED-CovidProject", "IEM_MED\n-CovidProject", model)) %>%
    mutate(model=ifelse(model=="COVIDhub-trained_ensemble", "COVIDhub\n-trained\n_ensemble", model))

  data_labels <-bind_rows( data_labels1,  data_labels4)

  return(data_labels)
  }
cov.plot <-function(df, df2) {
  ggplot(df) +
    geom_line(data=filter(df, bold=="F"), 
              mapping=aes(expected_cov, observed_cov, group=model, color=grouping, size=bold, alpha=0.75)) +
    geom_point(data=filter(df, bold=="F"), 
               mapping=aes(expected_cov, observed_cov, group=model, color=grouping), size=1.5) +
    geom_line(data=filter(df, bold=="T"), 
              mapping=aes(expected_cov, observed_cov, group=model, color=grouping, size=bold, alpha=0.75)) +
    geom_point(data=filter(df, bold=="T"), 
               mapping=aes(expected_cov, observed_cov, group=model, color=grouping), size=3) +
    geom_line(aes(expected_cov, expected_cov, color=grouping, group=model), linetype="dashed", size=1.5, color="black") +
    scale_size_manual(values = c("T"=1.5, "F"=0.85)) +
    scale_colour_manual(values = c("COVIDhub-baseline"="#762a83",
                                   "COVIDhub-4_week_ensemble"="#1b7837",
                                   "Other teams"="grey70"),
                        labels=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week\n_ensemble"),
                        breaks=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week_ensemble")) +
    guides(size = "none", alpha="none") +
    labs(y="Observed Coverage") +
    theme_bw()  + 
    theme(legend.position = "none", 
          axis.title.x = element_blank()) +
    geom_text_repel(data=df2,
                    mapping=aes(expected_cov, observed_cov, label=model), size=3,
                    force=1, point.padding=unit(0.5,'lines'), nudge_x =0.1,
                    segment.size= 0.05,  segment.color="grey50",
                    direction="y", #hjust = "right",
                    vjust=0.5) +
    scale_x_continuous(expand = expansion(mult = c(0.05, 0.25)))
}

# Figures

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")

coverage_US <-cov.fig_dat(filter(dat_US_state, location=="US", sub_date <= cut_date,
                                   !grepl("2", target),
                                   !grepl("3", target)))
labels_US <-data_labels(coverage_US)
Cov.Nat <-cov.plot(coverage_US, labels_US) +
  facet_wrap(~target) +
  theme(legend.position = c(0.02, 0.85), legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.5,1,1,1)),
        legend.key = element_rect(colour = NA, fill = NA),
        strip.text=strip.text_standard, strip.background=strip.background_standard) +
  labs(title="A. Coverage for National Forecasts")

coverage_states <-cov.fig_dat(filter(dat_US_state, location!="US", sub_date <= cut_date,
                                   !grepl("2", target),
                                   !grepl("3", target)))
labels_states <-data_labels(coverage_states)
Cov.State <-cov.plot(coverage_states, labels_states) +
  facet_wrap(~target) +
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard) +
  labs(title="B. Coverage for National State/Territory/DC Forecasts")

# Largest Counties
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date,
                                   !grepl("2", target),
                                   !grepl("3", target)))
labels_count <-data_labels(coverage_count) 
Cov.Co <-cov.plot(coverage_count, labels_count) +
  facet_wrap(~target) +
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard) +
  labs(title="C. Coverage for Large County Forecasts*",
       x="Expected Coverage")

```

```{r Fig S5.1, echo=FALSE, warning=F, message=F, fig.height=12, fig.width=12}

annotate_figure(
  grid.arrange(Cov.Nat, Cov.State, Cov.Co, ncol=1),
 bottom = text_grob("*U.S. counties with a population of at least 93,230 people ", hjust=1, x=1, face = "italic", size = 10))

```

####  Absolute WIS

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hide'}

# Function for WIS over time
WIS.ot.fig_dat <-function(df) {

  sub_date <-c(unique(df$sub_date))
  model <-c(as.character(unique(df$model)))
  model_dates <-crossing(sub_date, model)

  cast_dates <-df %>%
    dplyr::select(sub_date, date, target) %>%
    distinct() %>%
    left_join(model_dates, by="sub_date")

  dat <-df %>%
    full_join(cast_dates, ., by=c("model", "sub_date", "date", "target")) %>%
    mutate(bold=ifelse(model=="COVIDhub-baseline" | model=="COVIDhub-4_week_ensemble", "T", "F")) %>%
    group_by(model, date, bold, target) %>%
    summarize(abWIS=mean(interval_score, na.rm=TRUE)) %>%
    ungroup() %>%
    mutate(grouping=ifelse(model=="COVIDhub-baseline", "COVIDhub-baseline", 
                           ifelse(model=="COVIDhub-4_week_ensemble", "COVIDhub-4_week_ensemble", "Other teams"))) #%>%
  return(dat)

}
cov.ot.fig_dat <-function(df) {

  sub_date <-c(unique(df$sub_date))
  model <-c(as.character(unique(df$model)))
  model_dates <-crossing(sub_date, model)

  cov <-df %>%
    group_by(model, target_end_date, target) %>%
    coverage(df=.) %>%
    summarize(cov.95=mean(coverage.95))

  dat <-df %>%
    dplyr::select(sub_date, target_end_date, target) %>%
    distinct() %>%
    left_join(., model_dates, by=c("sub_date")) %>%
    dplyr::select(-sub_date) %>%
    left_join(., cov, by=c("model", "target_end_date", "target")) %>%
    distinct() %>%
    ungroup() %>%
    mutate(grouping=ifelse(model=="COVIDhub-baseline", "COVIDhub-baseline", 
                           ifelse(model=="COVIDhub-4_week_ensemble", "COVIDhub-4_week_ensemble", "Other teams"))) %>%
    mutate(bold=ifelse(model=="COVIDhub-baseline" | model=="COVIDhub-4_week_ensemble", "T", "F"))

  return(dat)

}
ot.plot <-function(df, x, y) {

  ggplot() +
    geom_line(data=filter(df, bold=="F"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    geom_point(data=filter(df, bold=="F"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    geom_line(data=filter(df, bold=="T"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    geom_point(data=filter(df, bold=="T"), mapping=aes({{x}}, {{y}}, group=model, color=grouping, size=bold)) +
    scale_size_manual(values = c("T"=1.25, "F"=0.85)) +
    scale_x_date(date_labels="%b-%y", breaks = df$x, date_breaks ="3 months", date_minor_breaks ="1 month") +
    geom_vline(xintercept = as.numeric(cut_date),  linetype=4, size=1.05) +
    scale_colour_manual(name="",
                        values = c("COVIDhub-baseline"="#762a83",
                                   "COVIDhub-4_week_ensemble"="#1b7837",
                                   "Other teams"="grey80"),
                        labels=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week_ensemble"),
                        breaks=c("Other teams", "COVIDhub-baseline", "COVIDhub-4_week_ensemble")) +
    guides(size = "none") + 
    theme_bw() +
    theme(legend.position = "none", 
          axis.title.x = element_blank())
}

###########################################################################
############################################################################

### WIS Over time
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")

## National
WIS_ot_nat <-WIS.ot.fig_dat(filter(WIS_all, location_name=="National",
                                   !grepl("2", target),
                                   !grepl("3", target))) 
Fig2.B <-ot.plot(WIS_ot_nat, date, abWIS)  +
   facet_wrap(~ target) +
  scale_y_continuous(trans='log10') +
  theme(axis.title.x=element_blank(),
        legend.position = c(0.02, 0.80),legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.25,0.25,0.25,0.25)),
        legend.key = element_rect(colour = NA, fill = NA),
        strip.text=strip.text_standard, strip.background=strip.background_standard) +
  labs(title="A. Average Weighted Interval Score for National Forecasts",
       y = "Average Weighted Interval Score") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.35))) + 
  theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

## State/Territory/District
WIS_ot_state <-WIS.ot.fig_dat(filter(WIS_all, location_name!="National",
                                     location_name!="American Samoa",
                                     !grepl("2", target),
                                     !grepl("3", target))) 
Fig2.C <-ot.plot(WIS_ot_state, date, abWIS) +
   facet_wrap(~ target) +
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard) +
  scale_y_continuous(trans='log10') +
  labs(title = "B. Average Weighted Interval Score for State/Territory/DC Forecasts",
       y = "Average Weighted Interval Score") + theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

## Large Counties
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.Rdata")
WIS_ot_co <-WIS.ot.fig_dat(filter(WIS_all, 
                                  !grepl("2", target),
                                  !grepl("3", target))) 
Fig2.D <-ot.plot(WIS_ot_co, date, abWIS) +
  facet_wrap(~ target) +
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard) +
  scale_y_continuous(trans='log10') +
  labs(title = "C. Average Weighted Interval Score for Large County Forecasts*",
       x = "Forecast target date",
       y = "Average Weighted Interval Score") + 
  theme(axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

############################################################################
############################################################################

### Coverage Over time

load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")

## National
cov_ot_nat <-cov.ot.fig_dat(filter(dat_US_state, location=="US", sub_date <= cut_date,
                                  !grepl("2", target),
                                  !grepl("3", target)))
Fig2.F <-ot.plot(cov_ot_nat, target_end_date, cov.95)  +
  geom_hline(yintercept = 0.95,  linetype=6, size=1.05) +
  facet_wrap(~ target) +
  theme(axis.title.x=element_blank()) +  
  labs(title="D. 95% Coverage for National Forecasts",
       y = "95% Coverage") + 
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

## State/Territory/District
cov_ot_state <-cov.ot.fig_dat(filter(dat_US_state, location!="US", sub_date <= cut_date, 
                                  !grepl("2", target),
                                  !grepl("3", target)))
Fig2.G <-ot.plot(cov_ot_state, target_end_date, cov.95) +
  facet_wrap(~ target) +
  geom_hline(yintercept = 0.95,  linetype=6, size=1.05) +
  labs(title = "E. 95% Coverage for State/Territory/DC Forecasts",
       y = "95% Coverage") + 
    theme(strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))
## Large Counties
cov_ot_co <-cov.ot.fig_dat(filter(dat_large_count, sub_date <= cut_date, 
                                  !grepl("2", target),
                                  !grepl("3", target)))
Fig2.H <-ot.plot(cov_ot_co, target_end_date, cov.95) +
  facet_wrap(~ target) +
  geom_hline(yintercept = 0.95,  linetype=6, size=1.05) +
  labs(title = "F. 95% Coverage for Large County Forecasts*",
       x = "Forecast target date",
       y = "95% Coverage") +  
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5))

```

```{r Fig S5.2, echo=FALSE, warning=FALSE, message=FALSE, fig.height=11, fig.width=12}

annotate_figure(
  grid.arrange(Fig2.B, Fig2.F,
             Fig2.C, Fig2.G,
             Fig2.D, Fig2.H,
             ncol=2),
          bottom = text_grob("*U.S. counties with a population of at least 93,230 people ", hjust=1, x=1, face = "italic", size = 10))

```

### Relative WIS

```{r Fig S5.3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=12.5}

# Forecasts
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")

###
relWIS <-WIS_all %>%
  filter(!grepl("2", target),
         !grepl("3", target)) %>%
  filter(type=="quantile") %>%
    summarise_scores(by = c("model", "location_name", "target"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
  mutate(scaled_rel_skill=round(scaled_rel_skill, 1),
         log_WIS=log2(scaled_rel_skill),
         location_name=as.character(location_name))

###
levels_model <-WIS_all %>%
  filter(type=="quantile") %>%
    summarise_scores(by = c("model"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    ungroup() %>% 
  mutate(model_reorder = fct_reorder(model, scaled_rel_skill, .desc = TRUE)) 
levels_model <-levels(levels_model$model_reorder)

Locations <-relWIS %>%
  dplyr::select(location_name) %>%
  distinct()

Models <-relWIS %>%
  dplyr::select(model, target) %>%
  distinct()

Locations_models <-crossing(Locations, Models) 
relWIS <- Locations_models %>%
  left_join(., relWIS) %>%
  ungroup() %>%
  mutate(model_reorder=factor(model, levels=levels_model))

# Reorder x and y axes
relWIS$location_name <-as.factor(relWIS$location_name)
relWIS$location_name <-relevel(relWIS$location_name, ref="National")
relWIS$location_name <-fct_rev(relWIS$location_name)

# Figure
ggplot(relWIS, aes(model_reorder, location_name)) +
  geom_tile(aes(fill=log_WIS)) +
  geom_text(aes(label=scaled_rel_skill), size=3) +
  facet_wrap(~target) +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 0, na.value = "grey75", 
                       name = "Relative \nWeighted Interval Score", 
                       breaks = c(-1,0,1,2), 
                       labels =c("0.5", 1, 2, 3)) + 
  theme_bw() +
  labs(fill="Relative \nWeighted Interval Score") +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1),
        axis.title.y = element_blank(),
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.text=axis.text_standard, plot.caption = plot.caption_standard)

```

### 2023-02-02 Code/Supplement 6_figures.Rmd
all code and figures

--- 2023-02-02 Code/Supplement 1A_figures.Rmd
@@
 ---
-title: "Supplement 1A"
+title: "Supplement 6"
 author: "VKL"
@@
 
+library(grid)
+
 setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")
-
-### Need functions
-source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage
-### Estimate Relative WIS 
-pairWIS_fun <-function(x, df) {
-
-  df <-df %>%
-    pairwise_comparison(., summarise_by = c("model"),
-                        baseline = "COVIDhub-baseline") %>%
-    dplyr::select(model, scaled_rel_skill) %>%
-    distinct()
-}
-pairWIS_co_fun <-function(x, df) {
-
-  df <-df %>%
-    pairwise_comparison(., summarise_by = c("model", "pop_size_quant2"),
-                        baseline = "COVIDhub-baseline") %>%
-    dplyr::select(model, pop_size_quant2, scaled_rel_skill) %>%
-    distinct()
-}
 
@@
 
-## Change labels for counties
- rename_counts <-function(df) {   
-   df <-df %>%
-     mutate(pop_size_quant2=ifelse(pop_size_quant2==1, "County Forecasts: Size Quantile 1",
-                                 ifelse(pop_size_quant2==2, "County Forecasts: Size Quantile 2",
-                                        ifelse(pop_size_quant2==3, "County Forecasts: Size Quantile 3", 
-                                               ifelse(pop_size_quant2==4, "County Forecasts: Size Quantile 4", "County forecasts: Size Quantile 5")))))
-}
-
 ```
@@
 
-### Supplement 1
+### Supplement 6
 
-```{r Fig S1A, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=11}
-start_date <-as.Date('2020-07-28')
-stop_date <-as.Date('2021-12-21')
+```{r echo=FALSE, warning=F, message=F}
 
-sec_models <-c("CU-nochange",  "CU-scenario_high", "CU-scenario_low", "CU-scenario_mid", "COVIDhub_CDC-ensemble") ## Non-primary models should be exlcuded
+load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_gee.Rdata") # data
+load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/model_caseslogstd_noint_gee.rda")
 
-## Must have 4 weeks of forecasts for all locations
-include_wks <-function(x, df){
+WIS_gee <-WIS_gee %>%
+  group_by(model) %>%
+  mutate(WIS_log_std=(log(interval_score)-mean(log(interval_score)))/sd(log(interval_score)),
+         cases_log_std=(log(true_value)-mean(log(true_value)))/sd(log(true_value))
+  ) %>%
+  ungroup()
 
-  df <-df %>%
-    group_by(model, sub_date, location) %>%
-    mutate(no_horizons=length(unique(target))) %>% 
-    ungroup() %>%
-    filter(no_horizons>=4) #There should be at least 4 horizons
-}
+team <-c(unique(as.character(WIS_gee$model))) 
+dat_team <-list()
+means_sds <-list()
+marg_means <-list()
 
-## Must have quantities for all forecasts
-include_quant <-function(x, df){
+# Model Predictions 
+for(i in 1:length(team)){
 
-  df <-df %>%
-    group_by(model, location, forecast_date, target) %>%
-    mutate(quants=length(quantile[!is.na(quantile)])) %>%
-    ungroup() %>%
-    filter(quants==7) #There should be 7 quantiles
+  dat_team[[i]] <-as.data.frame(WIS_gee %>%
+                                  filter(model==team[i]) %>%
+                                  mutate(model=droplevels(model)) %>%
+                                  ungroup())
 
-}
-
-## Must have forecasts for at least 50 locations for states/territories/district and national
-include_locs <-function(x, df){
-
-  df <-df %>%
-    mutate(location=as.factor(location)) %>%
-    group_by(model, forecast_date) %>%
-    mutate(locs=length(unique(location))) %>% #[quantile==0.5 & target=="1 wk ahead inc case"]))) %>%
-    ungroup() %>%
-    filter(locs>=50)
-
-}
-
-## Must have 75% of all counties per quantile per submission date forecasted
-include_locs_co <-function(x, df){
-
-  df <-df %>%
-    group_by(pop_size_quant2) %>%
-    mutate(locs_total=length(unique(location))) %>% 
-    ungroup() %>%
-    group_by(model, pop_size_quant2, sub_date) %>%
-    mutate(locs=length(unique(location))) %>% #[quantile==0.5 & target=="1 wk ahead inc case"]))) %>%
-    ungroup() %>%
-    mutate(percent_co=locs/locs_total) %>%
-    filter(percent_co>=0.75)
-}
-
-## Must have submitted at least 50% of weeks
-include_subs <-function(x, df){
-
-  df <-df %>%
-    filter(sub_date >= start_date) %>%
-    mutate(total=length(unique(sub_date))) %>% 
-    group_by(model) %>%
-    mutate(subs=length(unique(sub_date))) %>%
-    ungroup() %>%
-    mutate(percent_sub=subs/total) %>%
-    filter(percent_sub>=0.50)
-
-}
-
-############################################################################
-############################################################################
-
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/updated_cases_nat_state_forecasts_2022-04-04.Rdata")
-
-### National + state submissions
-nat_st <-all_dat %>%
-  filter(!(model %in% sec_models),
-         sub_date >= start_date & sub_date <= stop_date) %>%
-  filter(type=="point")
-
-### National + state submissions that met inclusion criteria
-teams_nat_st <-all_dat %>%
-  filter(!(model %in% sec_models),
-         sub_date >= start_date & sub_date <= stop_date) %>%
-  include_quant(df=.) %>% #all quantiles present
-  include_wks(df=.) %>% #all targets included 
-  include_locs(df=.) %>% #at least 50 locations
-  include_subs(df=.) %>% #submitted at least 50% of the time
-  dplyr::select(model) %>%
-  mutate(model_rename=paste0("*", model)) %>%
+  means_sds[[i]] <-dat_team[[i]] %>%
+    mutate(mean_log_WIS=mean(log(interval_score)),
+           sd_log_WIS=sd(log(interval_score)),
+           mean_log_cases=mean(log(true_value)),
+           sd_log_cases=sd(log(true_value))
+    ) %>%
+    dplyr::select(model, contains("mean_"), contains("sd_")) %>%
     distinct()
 
-### Submission plots
+  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase_all", "cases_log_std[-1.96:1.96]")) %>%
+    rename(phase_all=x,
+           cases=group) %>% 
+    mutate(model=team[i],
+           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
+           predicted_back_lo=(conf.low*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
+           predicted_back_up=(conf.high*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
+           cases=as.numeric(as.character(cases)),
+           cases_log_back=(cases*means_sds[[i]]$sd_log_cases) + means_sds[[i]]$mean_log_cases) %>%
+    mutate(predicted_back_rescale=exp(predicted_back),
+           predicted_back_lo_rescale=exp(predicted_back_lo),
+           predicted_back_up_rescale=exp(predicted_back_up),
+           cases_back_rescale=exp(cases_log_back))
+}
+marg_means <-do.call(rbind.data.frame, marg_means)
 
-nat_st %>%
-  dplyr::select(-target, -target_end_date, -value) %>%
-  distinct() %>%
-  group_by(sub_date, model) %>%
-  summarize(locs=n()) %>%
-  ungroup() %>%
-  mutate(log_loc=log(locs)) %>%
-  ungroup() %>%
-  mutate(total_sub=length(unique(sub_date))) %>%
-  group_by(model) %>%
-  mutate(wks_sub=length(sub_date),
-         per_sub=wks_sub/total_sub) %>%
-  ungroup() %>%
-  left_join(., teams_nat_st, by="model") %>%
-  mutate(model_rename=ifelse(is.na(model_rename), model, model_rename),
-         model_rename=fct_reorder(model_rename, wks_sub)) %>%
-  ggplot(., aes(sub_date, model_rename)) +
-  geom_tile(aes(fill=log_loc)) +
-  scale_fill_gradient(low = "#c7e9c0", high = "#41ab5d") + 
-  geom_text(aes(label=locs), size=1.50) +
-  scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%B") +
+marg_means <-marg_means %>%
+
+  mutate(model=as.factor(model)) %>%
+  mutate(phase_all=as.factor(ifelse(phase_all=="increasing", "Increasing",
+                                    ifelse(phase_all=="decreasing", "Decreasing",
+                                           ifelse(phase_all=="peak", "Peak", "Nadir")))),
+         phase_all=factor(phase_all, 
+                          levels = c("Increasing", "Peak", "Decreasing",  "Nadir"))
+  )
+
+# Figure
+FigS6 <-marg_means %>%
+  ggplot(., aes(cases_back_rescale, predicted_back_rescale)) +
+  geom_line(aes(color=phase_all)) +
+  geom_ribbon(aes(ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale, fill=phase_all), alpha=0.35) +
+  scale_fill_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 
+                      values=c("#fdae61", "#abdda4", "#bababa", "#d7191c", "#2b83ba")) +
+  scale_color_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 
+                      values=c("#fdae61", "#abdda4", "#bababa", "#d7191c", "#2b83ba")) +
+  labs( y="Marginal Mean \nWeighted Interval Score", x="Reported cases") +
+  facet_wrap(~model) +
   theme_bw() +
-  labs(title = "A. Primary Model* Submissions for National/State/Territory-Level Case Forecasts Over Time",
-       subtitle= "The number of locations forecasted per submission is labled",
-       caption = "*Model met inclusion criteria") +
-  theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1),
-        axis.title.y = element_blank(),
-        legend.position = "none")
+  theme(axis.title.y=axis.title.y_standard,
+        legend.title = element_blank(), legend.text=legend.text_standard,
+        strip.text=strip.text_standard, strip.background=strip.background_standard,
+        axis.text.x = element_text(angle = 45, hjust=1)) +
+  guides(fill=guide_legend(nrow=2, byrow=TRUE))
 
 ```
+
+```{r Fig s6, echo=FALSE, warning=F, message=F, fig.height=8, fig.width=11.5}
+
+grid.draw(shift_legend(FigS6))
+
+```

### 2023-02-02 Code/Apply_inclusion_criteria.R

@@ -9,7 +9,7 @@ start_date <-as.Date('2020-07-28')
 stop_date <-as.Date('2021-12-21')
 
 ## Non-primary models should be exlcuded
-sec_models <-c("CU-nochange",  "CU-scenario_high", "CU-scenario_low", "CU-scenario_mid", "COVIDhub_CDC-ensemble")
+sec_models <-c("CU-nochange",  "CU-scenario_high", "CU-scenario_low", "CU-scenario_mid", "COVIDhub_CDC-ensemble") #Note ensemble replaced with 4_week ensemble
 
 ## Must have 4 weeks of forecasts for all locations
 include_wks <-function(x, df){
@@ -38,7 +38,7 @@ include_locs <-function(x, df){
   df <-df %>%
     mutate(location=as.factor(location)) %>%
     group_by(model, forecast_date) %>%
-    mutate(locs=length(unique(location))) %>% #[quantile==0.5 & target=="1 wk ahead inc case"]))) %>%
+    mutate(locs=length(unique(location))) %>% 
     ungroup() %>%
     filter(locs>=50) 
   
@@ -52,7 +52,7 @@ include_locs_co <-function(x, df){
     mutate(locs_total=length(unique(location))) %>% 
     ungroup() %>%
     group_by(model, pop_size_quant2, sub_date) %>%
-    mutate(locs=length(unique(location))) %>% #[quantile==0.5 & target=="1 wk ahead inc case"]))) %>%
+    mutate(locs=length(unique(location))) %>% 
     ungroup() %>%
     mutate(percent_co=locs/locs_total) %>%
     filter(percent_co>=0.75)

### 2023-02-02 Code/Reported cases.R

@@ -1,0 +1,65 @@
+library(tidyverse)
+
+rd_obs <-function(){
+  
+  # Pulls population information from CSSE
+  pop.state <-read.csv('https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv') %>%
+    rename(location_name = "Province_State",
+           population = "Population") %>%
+    filter(location_name!="Diamond Princess", location_name!="Grand Princess") %>%
+    mutate(id = ifelse(nchar(FIPS)==4, paste("0", FIPS, sep = ""), #To adjust for location_names with fips codes < 10
+                       ifelse(nchar(FIPS)==2, paste(FIPS, "000", sep = ""), FIPS)), #to adjust for territories
+           location = substr(id, 1, 2)) %>%
+    dplyr::select(location_name, population, location) %>%
+    filter(population > 0) %>% #oddly KA City,MO is not given a fips code?
+    mutate(location = ifelse(location_name=="Missouri" & is.na(location), '29', location)) %>%
+    group_by(location_name, location) %>%
+    summarise(population = sum(population)) %>% 
+    ungroup() %>% 
+    add_row(location="US",
+            location_name="National",
+            population=0) %>%
+    mutate(population = ifelse(location=='US', sum(population), population)) 
+  
+  start_date <-as.Date("2020-07-28")
+  end_date <-as.Date("2022-03-19")
+  
+  # Reported cases counts from Forecast hub as of April 2, 2022
+  obs_data <- read_csv("C:/Users/oko8/OneDrive - CDC/Projects/covid19-forecast-hub/data-truth/truth-Incident Cases.csv") %>%
+    mutate(wk_end_date = as.Date(date, "%m/%d/%y"),
+           wk_end_date=as.Date(cut(wk_end_date,"week", start.on.monday = FALSE)) + 6) %>% #,
+           #value=ifelse(value < 0, 0, value)) %>%
+    group_by(location_name, location, wk_end_date) %>%
+    summarize(true_value=sum(value)) %>%
+    rename(date=wk_end_date) %>%
+    arrange(location_name, date) %>%
+    mutate(location_name=ifelse(location_name=="United States", "National", location_name),
+           grouping=ifelse(location_name=="National", "National", "State/Territory/DC")) %>%
+    filter(date > start_date) %>%
+    filter(date <= end_date) %>%
[…]

### 2023-02-02 Code/Supplement 4_Rt_Epi Phases.R

@@ -1,0 +1,318 @@
+library(tidyverse)
+library(zoo)
+library(data.table)
+library(mgcv)
+library(purrr)
+library(slider)
+
+####--- Read in Rt Data ---####
+
+setwd("C:/Users/oko8/OneDrive - CDC/Projects/epiforecasts_all_versions_rt/all_versions_exported")
+
+## Need to update all file names since non alpha-numeric characters were included in the title (note, first needed to truncate names in the CMB with "ren *.* ??????????-test.*")
+datapath <-"C:/Users/oko8/OneDrive - CDC/Projects/epiforecasts_all_versions_rt/all_versions_exported"
+fileList <-dir(path = datapath, pattern = '*.csv')  # list of file names, not including their paths
+
+sapply(X = fileList, FUN = function(x) {
+  file.rename(paste0(datapath, x),     # paste0() the path and old name
+              paste0(datapath, substr(x, 1, 10), ".csv")) })
+
+read_file_name <- function(flnm) {
+  read_csv(flnm) %>% 
+    mutate(file_date = flnm)
+}
+
+rt <-list.files(pattern = "*.csv", 
+             full.names = T) %>% 
+  map_df(~read_file_name(.) %>%
+           filter(type=="estimate") 
+  )
+
+####--- Pull midweek estimates and calculate means per date ---####
+
+## Pick midweek estimates for all submissions
+rt <-rt %>%
+  mutate(median=as.numeric(median),
+         mean=as.numeric(mean),
+         sd=as.numeric(sd),
+         upper_90=as.numeric(upper_90),
+         lower_90=as.numeric(lower_90),
+         date=as.Date(date, "%m/%d/%Y"),
+         file_date=gsub(".csv","", file_date),
+         file_date=gsub("./","", file_date), 
+         state=ifelse(is.na(state), region, state),
+         wk_day=weekdays(as.Date(date))) %>%
+  filter(wk_day=="Wednesday",
+         state!="Northern Mariana Islands",
+         state!="Guam",
+         state!="American Samoa") %>%
+  dplyr::select(file_date, state, date, mean, median, lower_90, upper_90)
+
+
+## Median values per date
+rt_med <-rt %>%
+  group_by(state, date) %>%
+  summarize(median_med=median(median, na.rm=TRUE),
+            lower_90_med=median(lower_90, na.rm=TRUE),
[…]

### 2023-02-02 Code/create_WIS_non large counties.R

@@ -12,19 +12,9 @@ obs_data <-rd_obs() %>%
   dplyr::select(location_name, date, true_value)
 
 ####--- Estimate WIS ---####
-US_models <-function() {
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
-  US_models <- dat_US_state %>%
-    filter(location=="US") %>%
-    dplyr::select(model) %>% 
-    distinct()
-}
-US_models <-US_models()
-  
 dat <-function() {
   load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")
   dat <-dat_other_count %>%
-    #filter(model %in% US_models$model) %>% #filter to reduce size for non large counties
     filter(sub_date <= cut_date)
 }
 

### 2023-03-14 Code/Manuscript_figures.Rmd
updated figures after coauthor review

@@
   labs(title = "A. Reported Cases Per 100K Population",
-       y = "Incident COVID-19 Cases") +
+       y = "Incident COVID-19 Cases per 100K population") +
   theme_bw() +
@@
   theme_bw() +
-  labs(fill="Relative Weighted Interval Score") +
+  labs(fill="Relative Weighted Interval Score",
+       title="B. Relative Weighted Interval Score") +
   theme(axis.title.x = element_blank(), 
@@
   theme_bw() +
-  labs(fill="95% Coverage") +
+  labs(fill="95% Coverage",
+       title="C. 95% Coverage") +
   theme(axis.title.x = element_blank(), #axis.text.x = element_text(angle = 45, hjust=1),
@@
   theme_bw() +
-  labs(fill="% Weeks \nSubmitted") +
+  labs(fill="% Weeks \nSubmitted",
+       title="A. Percent of Weeks Submitted") +
   theme(axis.title.x = element_blank(), 
@@
   labs(y="", title="B.",
-       caption="*Probability >= 0.90 that forecasts outperform baseline") + 
+       caption="*80% CI is lower than baseline") + 
   theme_bw() +

### 2023-03-14 Code/Supplement 1A_figures.Rmd
updated figures after coauthor review

@@
 
-### Need functions
-source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage
-### Estimate Relative WIS 
-pairWIS_fun <-function(x, df) {
-
-  df <-df %>%
-    pairwise_comparison(., summarise_by = c("model"),
-                        baseline = "COVIDhub-baseline") %>%
-    dplyr::select(model, scaled_rel_skill) %>%
-    distinct()
-}
-pairWIS_co_fun <-function(x, df) {
-
-  df <-df %>%
-    pairwise_comparison(., summarise_by = c("model", "pop_size_quant2"),
-                        baseline = "COVIDhub-baseline") %>%
-    dplyr::select(model, pop_size_quant2, scaled_rel_skill) %>%
-    distinct()
-}
-
 ## Standardized formatting
@@
   geom_tile(aes(fill=log_loc)) +
-  scale_fill_gradient(low = "#c7e9c0", high = "#41ab5d") + 
-  geom_text(aes(label=locs), size=1.50) +
+  scale_fill_gradient(low = "#c7e9c0", high = "#41ab5d",
+                      name = "Number of \nlocations forecasted", 
+                      breaks = c(0, 3.9), 
+                      labels =c(1, 50)
+                      ) + 
+ # geom_text(aes(label=locs), size=1.50) +
   scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%B") +
@@
   labs(title = "A. Primary Model* Submissions for National/State/Territory-Level Case Forecasts Over Time",
-       subtitle= "The number of locations forecasted per submission is labled",
-       caption = "*Model met inclusion criteria") +
+       #subtitle= "The number of locations forecasted per submission is labled"#,
+       caption = "*Model met inclusion criteria"
+       ) +
   theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1),
         axis.title.y = element_blank(),
-        legend.position = "none")
+        legend.position = "bottom", legend.title.align=0.5)
 

### 2023-03-14 Code/Supplement 1B_figures.Rmd
updated figures after coauthor review

@@
 library(gridExtra)
+library(grid)
 
@@
 setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")
-
-### Need functions
-source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage
 
@@
 axis.text_standard <-element_text(size=11)
+
+## Function for setting up legends in empty facet spaces
+library(gtable)
+library(cowplot)
+
+shift_legend <- function(p){
+
+  # check if p is a valid object
+  if(!"gtable" %in% class(p)){
+    if("ggplot" %in% class(p)){
+      gp <- ggplotGrob(p) # convert to grob
+    } else {
+      message("This is neither a ggplot object nor a grob generated from ggplotGrob. Returning original plot.")
+      return(p)
+    }
+  } else {
+    gp <- p
+  }
+
+  # check for unfilled facet panels
+  facet.panels <- grep("^panel", gp[["layout"]][["name"]])
+  empty.facet.panels <- sapply(facet.panels, function(i) "zeroGrob" %in% class(gp[["grobs"]][[i]]))
+  empty.facet.panels <- facet.panels[empty.facet.panels]
+  if(length(empty.facet.panels) == 0){
+    message("There are no unfilled facet panels to shift legend into. Returning original plot.")
+    return(p)
+  }
+
+  # establish extent of unfilled facet panels (including any axis cells in between)
+  empty.facet.panels <- gp[["layout"]][empty.facet.panels, ]
+  empty.facet.panels <- list(min(empty.facet.panels[["t"]]), min(empty.facet.panels[["l"]]),
+                             max(empty.facet.panels[["b"]]), max(empty.facet.panels[["r"]]))
+  names(empty.facet.panels) <- c("t", "l", "b", "r")
+
+  # extract legend & copy over to location of unfilled facet panels
+  guide.grob <- which(gp[["layout"]][["name"]] == "guide-box")
+  if(length(guide.grob) == 0){
+    message("There is no legend present. Returning original plot.")
+    return(p)
+  }
+  gp <- gtable_add_grob(x = gp,
+                        grobs = gp[["grobs"]][[guide.grob]],
+                        t = empty.facet.panels[["t"]],
+                        l = empty.facet.panels[["l"]],
+                        b = empty.facet.panels[["b"]],
+                        r = empty.facet.panels[["r"]],
+                        name = "new-guide-box")
+
+  # squash the original guide box's row / column (whichever applicable)
+  # & empty its cell
+  guide.grob <- gp[["layout"]][guide.grob, ]
+  if(guide.grob[["l"]] == guide.grob[["r"]]){
+    gp <- gtable_squash_cols(gp, cols = guide.grob[["l"]])
+  }
+  if(guide.grob[["t"]] == guide.grob[["b"]]){
+    gp <- gtable_squash_rows(gp, rows = guide.grob[["t"]])
+  }
+  gp <- gtable_remove_grobs(gp, "guide-box")
+
+  return(gp)
+}
 
@@
 
-counts %>%
+counts_subs <-counts %>%
   dplyr::select(-target, -target_end_date, -value) %>%
@@
 
+grid.draw(shift_legend(counts_subs))
+
 ```

### 2023-03-14 Code/Supplement 3.1_figure.rmd
updated figures after coauthor review

@@
   theme_bw() +
-  labs(fill="Relative Weighted Interval Score") +
+  labs(fill="Relative Weighted Interval Score",
+       title="B. Relative Weighted Interval Score") +
   theme(axis.title.x = element_blank(), axis.text.y=element_blank(),
@@
   theme_bw() +
-  labs(fill="95% Coverage") +
+  labs(fill="95% Coverage",
+       title="C. 95% Coverage") +
   theme(axis.title.x = element_blank(), 
@@
   theme_bw() +
-  labs(fill="% Weeks \nSubmitted") +
+  labs(fill="% Weeks \nSubmitted",
+       title="A. Percent of Weeks Submitted") +
   theme(axis.title.x = element_blank(),   

### 2023-04-18 Code/Manuscript_figures.Rmd
cleaned up code

@@
 
+library(here)
 library(tidyverse)
@@
 
-setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")
 cut_date <-as.Date("2021-12-21")
@@
 ### Need functions
-source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage
+source(here("Code/coverage.R")) #coverage
 
@@
 ### Reported cases over time
-source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/reported cases.R") #reported cases
+source(here("Code/Reported cases.R")) #reported cases
 obs_data <-rd_obs() %>%
@@
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
+load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))
 
@@
 mean_WIS <-function() {
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.rdata")
+  load(here("Data/WIS_all horizons_nat_state.rdata"))
 
@@
 
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
+  load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))
 
@@
 
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_2021-03-13.Rdata")
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_2022-03-21.Rdata")
+  load(here("Data/cases_nat_state_forecasts_2021-03-13.Rdata"))
+  load(here("Data/cases_nat_state_forecasts_2022-03-21.Rdata"))
 
@@
 # Figures
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
+load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))
 
@@
 # Largest Counties
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
+load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata"))
 coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date))
@@
 
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.rdata")
+  load(here("Data/WIS_all horizons_large counties.Rdata"))
 
@@
 
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_non large counties_all.Rdata")
+  load(here("Data/WIS_all horizons_non large counties_all.Rdata"))
   rel_WIS_co <-WIS_all %>%
@@
 # Forecasts
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")
+load(here("Data/WIS_all horizons_nat_state.Rdata"))
 
@@
 ### WIS Over time
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")
+load(here("Data/WIS_all horizons_nat_state.Rdata"))
 
@@
 ## Large Counties
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.Rdata")
+load(here("Data/WIS_all horizons_large counties.Rdata"))
 WIS_ot_co <-WIS.ot.fig_dat(WIS_all)
@@
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
+load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))
+load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata"))
 
@@
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_gee.Rdata") # data
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/gee_for_manuscript.rda")
+load(here("Data/WIS_gee.Rdata")) # data
+load(here("Data/gee_for_manuscript.rda"))
 
@@
   theme_bw() +
-  theme(axis.title.y=axis.title.y_standard, axis.text=axis.text_standard,
+  theme(axis.title.y=axis.title.y_standard, axis.text.y=axis.text_standard,
         legend.position = "bottom", legend.title = element_blank(), legend.text=legend.text_standard,
@@
         axis.title.x = element_blank(),
-        axis.text.x = element_text(angle = 45, hjust=1))
+        #axis.text.x = element_text(angle = 45, hjust=1),
+        axis.text.x = element_blank())
 
@@
 
-Fig7A_updated <-Fig7A + theme(axis.text.x = element_blank())
-
-plot_grid(Fig7A_updated, Fig7B, rel_heights  = c(0.5, 1), axis = "l",
+plot_grid(Fig7A, Fig7B, rel_heights  = c(0.5, 1), axis = "l",
           align="v", nrow = 2)

### 2023-04-18 Code/Supplement 1A_figures.Rmd
cleaned up code

@@
 library(splines)
-
-setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")
 
@@
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/updated_cases_nat_state_forecasts_2022-04-04.Rdata")
+load(here("Data/updated_cases_nat_state_forecasts_2022-04-04.Rdata"))
 

### 2023-04-18 Code/Supplement 1B_figures.Rmd
cleaned up code

@@
 library(scoringutils)
-
-setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")
 
@@
 ####
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_county_forecasts_2022-04-04.Rdata")
-size <-read.csv("C:/Users/oko8/Downloads/SVI2018_US_COUNTY.csv") %>%
+load(here("Data/cases_county_forecasts_2022-04-04.Rdata"))
+size <-read.csv(here("Data/SVI2018_US_COUNTY.csv")) %>%
   dplyr::select(FIPS, E_TOTPOP) %>%

### 2023-04-18 Code/Supplement 2_Outliers.Rmd
cleaned up code

@@
 ## rename locations based on state names
-states <-read.csv("C:/Users/oko8/OneDrive - CDC/Projects/covid19-forecast-hub/data-locations/locations.csv") %>%
+states <-read.csv(here("Data/locations.csv")) %>%
   rename(fips = location) %>%
@@
 ## Read in data
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_gee.Rdata")
+load(here("Data/WIS_gee.Rdata"))
 

### 2023-04-18 Code/Supplement 2_Revisions.Rmd
cleaned up code

@@
    mutate(location_name=droplevels(location_name))
-
-```
-
-```{r Fig S2.1, echo=FALSE, warning=FALSE, message=FALSE, fig.height=12, fig.width=20}
-
-main_dat <-main_dat %>%
-  mutate(geo_value=toupper(geo_value)) %>%
-  left_join(., states, by=c("geo_value"="abbreviation"))
-
-hx_dats_all %>%
-  mutate(geo_value=toupper(geo_value)) %>%
-  left_join(., states, by=c("geo_value"="abbreviation")) %>%
-  ungroup() %>%
-  ggplot(.) +
-  geom_line(aes(time_value, cases_last), color="#cb181d", alpha=0.55) + #as.factor(wk)),  alpha=0.65) +
-  geom_line(main_dat, mapping=aes(time_value, cases_now), size=0.65) +
-  facet_wrap(~ geo_value, scales="free_y") +
-  scale_x_date(date_labels="%b-%y", breaks = hx_dats_all$wk, date_breaks ="3 months", date_minor_breaks ="1 month") +
-  labs(y="Reported cases") +
-  theme_bw() +
-  theme(legend.position = "none", 
-        axis.title.x=element_blank(), axis.text.x=element_text(size=6),
-        strip.text=strip.text_standard, strip.background=strip.background_standard,
-        panel.border = element_rect(colour = "black", fill = NA))
 

### 2023-04-18 Code/Supplement 3.1_figure.rmd
cleaned up code

@@
 
-setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")
-
 ### Need functions
-source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/coverage.R") #coverage
+source(here("Code/coverage.R")) #coverage
 
@@
   ## Large counties
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.rdata")
+  load(here("Data/WIS_all horizons_large counties.rdata"))
 
@@
   ## Non Large counties
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_non large counties_all subs.rdata")
+  load(here("Data/WIS_all horizons_non large counties_all subs.rdata"))
 
@@
 cov.95 <-function() {
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
+  load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
 
@@
 
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")
+  load(here("Data/cases_non large counties_forecasts_for analysis_2022-08-18.rdata"))
 
@@
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
+load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
 subs_co <-submissions(df=dat_large_count) %>%
@@
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")
+load(here("Data/cases_non large counties_forecasts_for analysis_2022-08-18.rdata"))
 subs_co_other <-submissions(df=dat_other_count) %>%

### 2023-04-18 Code/Supplement 5_all figures.Rmd
updated figures after coauthor review
cleaned up code

@@
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
+load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.rdata"))
 
@@
 # Largest Counties
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
+load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
 coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date,
@@
 ### WIS Over time
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")
+load(here("Data/WIS_all horizons_nat_state.rdata"))
 
@@
 ## Large Counties
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_large counties.Rdata")
+load(here("Data/WIS_all horizons_large counties.rdata"))
 WIS_ot_co <-WIS.ot.fig_dat(filter(WIS_all, 
@@
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
+load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.rdata"))
+load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
 
@@
 
-```{r Fig S5.3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=12.5}
+```{r Fig S5.3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=15}
 
 # Forecasts
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.Rdata")
+load(here("Data/WIS_all horizons_nat_state.rdata"))
 

### 2023-04-18 Code/Supplement 6_figures.Rmd
cleaned up code

@@
 library(grid)
-
-setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts")
 
@@
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_gee.Rdata") # data
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/model_caseslogstd_noint_gee.rda")
-
-WIS_gee <-WIS_gee %>%
-  group_by(model) %>%
-  mutate(WIS_log_std=(log(interval_score)-mean(log(interval_score)))/sd(log(interval_score)),
-         cases_log_std=(log(true_value)-mean(log(true_value)))/sd(log(true_value))
-  ) %>%
-  ungroup()
+load(here("./Data/WIS_gee.Rdata")) # data
+load(here("./Data/gee_for_manuscript.rda"))
 
@@
 
-  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase_all", "cases_log_std[-1.96:1.96]")) %>%
-    rename(phase_all=x,
+  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase", "cases_log_std[-1.96:1.96]")) %>%
+    rename(phase=x,
            cases=group) %>% 
@@
   mutate(model=as.factor(model)) %>%
-  mutate(phase_all=as.factor(ifelse(phase_all=="increasing", "Increasing",
-                                    ifelse(phase_all=="decreasing", "Decreasing",
-                                           ifelse(phase_all=="peak", "Peak", "Nadir")))),
-         phase_all=factor(phase_all, 
+  mutate(phase=as.factor(ifelse(phase=="increasing", "Increasing",
+                                    ifelse(phase=="decreasing", "Decreasing",
+                                           ifelse(phase=="peak", "Peak", "Nadir")))),
+         phase=factor(phase, 
                           levels = c("Increasing", "Peak", "Decreasing",  "Nadir"))
@@
   ggplot(., aes(cases_back_rescale, predicted_back_rescale)) +
-  geom_line(aes(color=phase_all)) +
-  geom_ribbon(aes(ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale, fill=phase_all), alpha=0.35) +
+  geom_line(aes(color=phase)) +
+  geom_ribbon(aes(ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale, fill=phase), alpha=0.35) +
   scale_fill_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 

### 2023-04-18 Code/Apply_inclusion_criteria.R

@@ -78,7 +78,7 @@ include_subs <-function(x, df){
 ### Applying inclusion criteria
 
 ## National
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/updated_cases_nat_state_forecasts_2022-04-04.Rdata")
+load("./Data/updated_cases_nat_state_forecasts_2022-04-04.Rdata")
 
 dat_US_state <- all_dat %>%
 
@@ -91,11 +91,11 @@ dat_US_state <- all_dat %>%
   include_subs(df=.) %>%
   dplyr::select(-quants, -no_horizons, -locs, -total, -subs, -percent_sub)
 
-save(dat_US_state, file=paste0("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_",
+save(dat_US_state, file=paste0("./Data/cases_nat_state_forecasts_for analysis_",
                                Sys.Date(), ".Rdata"))
 
 ## Large counties
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_county_forecasts_2022-04-04.Rdata")
+load("./Data/cases_county_forecasts_2022-04-04.Rdata")
 
 # All inclusion criteria except for % of counties per pop size
 all_dat <-all_dat %>%
@@ -106,7 +106,7 @@ all_dat <-all_dat %>% include_wks(df=.)
 all_dat <-all_dat %>% include_subs(df=.) 
 
 # Inclusion criteria for counties based on pop size
-size <-read.csv("C:/Users/oko8/Downloads/SVI2018_US_COUNTY.csv") %>%
+size <-read.csv("./Data/SVI2018_US_COUNTY.csv") %>% #data source: https://www.atsdr.cdc.gov/placeandhealth/svi/data_documentation_download.html
   dplyr::select(FIPS, E_TOTPOP) %>%
   rename(location=FIPS) %>%
   mutate(location=as.character(location),
@@ -124,12 +124,12 @@ all_dat <-all_dat %>%
 dat_large_count <-all_dat %>%
   filter(pop_size_quant2==5) 
   
-save(dat_large_count, file=paste0("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_",
+save(dat_large_count, file=paste0("./Data/cases_large counties_forecasts_for analysis_",
                                   Sys.Date(), ".Rdata"))
 ## All other counties
[…]

### 2023-04-18 Code/GEE_models.R

@@ -1,17 +1,15 @@
 library(tidyverse)
 
-setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data")
-
 ####--- Data management ---####
 
-load("C:/Users/oko8/OneDrive - CDC/Projects/epiforecasts_all_versions_rt/all_versions_exported/rt3.rdata")
-phases <-rt3 %>%
+load("./Data/rt_phases.rdata")
+phases <-rt_phases %>%
   dplyr::select(date, location_name, location, phase, sum) %>%
   rename(true_value=sum)  %>%
   mutate(date=as.Date(date)+3) #Date = Wednesday, but need it to be on Saturday
-save(phases, file="covid_epi_phases.rdata")
+save(phases, file="./Data/covid_epi_phases.rdata")
 
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_nat_state.rdata")
+load("./Data/WIS_all horizons_nat_state.rdata")
 
 ### Analysis for phase at forecast prediction
 
@@ -34,7 +32,7 @@ WIS_gee <- WIS_all %>%
   ) %>%
   ungroup()
 
-save(WIS_gee, file="WIS_gee.rdata")
+save(WIS_gee, file="./Data/WIS_gee.rdata")
 
 ########################################
 ########################################
@@ -58,4 +56,4 @@ for(i in 1:length(team)){
                       corstr = "independence")  
 }
 
-save(model, file="gee_for_manuscript.rda")
+save(model, file="./Data/gee_for_manuscript.rda")

### 2023-04-18 Code/Reported cases.R

@@ -25,7 +25,7 @@ rd_obs <-function(){
   end_date <-as.Date("2022-03-19")
   
   # Reported cases counts from Forecast hub as of April 2, 2022
-  obs_data <- read_csv("C:/Users/oko8/OneDrive - CDC/Projects/covid19-forecast-hub/data-truth/truth-Incident Cases.csv") %>%
+  obs_data <- read_csv("./Data/truth-Incident Cases.csv") %>%
     mutate(wk_end_date = as.Date(date, "%m/%d/%y"),
            wk_end_date=as.Date(cut(wk_end_date,"week", start.on.monday = FALSE)) + 6) %>% #,
            #value=ifelse(value < 0, 0, value)) %>%

### 2023-04-18 Code/Supplement 2_CSSE revisions over time.R

@@ -1,0 +1,122 @@
+library(here)
+library(tidyverse)
+library(covidcast)
+library(epiprocess)
+
+library(gridExtra)
+library(grid)
+library(cowplot)
+
+
+## Standardized formatting
+strip.background_standard <-element_blank()
+strip.text_standard <-element_text(size = 8, face='bold')
+axis.title.y_standard <-element_text(margin = margin(1, 10, 1, 1), size=12)
+
+
+## Read in data used in analysis
+main_dat <-covidcast_signal(data_source = "jhu-csse",
+                            signal = "confirmed_incidence_num",
+                            start_day = "2020-07-26",
+                            end_day = "2022-01-15",
+                            geo_type = "state",
+                            as_of = "2022-04-02") %>%
+  dplyr::select(geo_value, time_value, cases_now=value) %>%   
+  filter(geo_value!="as", geo_value!="gu", geo_value!="mp",
+         geo_value!="pr", geo_value!="vi"#, geo_value!='dc'
+  ) %>% 
+  group_by(geo_value) %>%
+  mutate(final_wk="2022-04-02")
+
+dates <-seq.Date(as.Date("2020-08-01"), as.Date("2022-01-15"), by="week")
+hx_dat <-list()
+for(i in 1:length(dates)){
+  hx_dat[[i]] <-covidcast_signal(data_source = "jhu-csse",
+                                 signal = "confirmed_incidence_num",
+                                 start_day ="2020-07-26",
+                                 end_day = dates[[i]], 
+                                 geo_type = "state",
+                                 as_of = dates[[i]] +1) %>%
+    dplyr::select(geo_value, time_value, cases_last=value) %>%   
+    filter(geo_value!="as", geo_value!="gu", geo_value!="mp",
+           geo_value!="pr", geo_value!="vi"#, geo_value!='dc'
+    ) %>% 
+    mutate(wk = as.Date(time_value, "%m/%d/%y"), 
+           wk = as.Date(cut(wk,"week", start.on.monday = FALSE)) + 6, 
+           max_wk=max(wk)) %>%
+    left_join(., main_dat, by=c("time_value", "geo_value"))
+}
+
+hx_dats_all <-do.call(rbind, hx_dat)
+
+## rename locations based on state names
[…]

### 2023-04-18 Code/Supplement 4_Rt_Epi Phases.R

@@ -7,26 +7,18 @@ library(slider)
 
 ####--- Read in Rt Data ---####
 
-setwd("C:/Users/oko8/OneDrive - CDC/Projects/epiforecasts_all_versions_rt/all_versions_exported")
-
 ## Need to update all file names since non alpha-numeric characters were included in the title (note, first needed to truncate names in the CMB with "ren *.* ??????????-test.*")
-datapath <-"C:/Users/oko8/OneDrive - CDC/Projects/epiforecasts_all_versions_rt/all_versions_exported"
+datapath <-"./Data/epiforecasts_all_versions_rt/all_versions_exported/"
 fileList <-dir(path = datapath, pattern = '*.csv')  # list of file names, not including their paths
 
-sapply(X = fileList, FUN = function(x) {
-  file.rename(paste0(datapath, x),     # paste0() the path and old name
-              paste0(datapath, substr(x, 1, 10), ".csv")) })
-
-read_file_name <- function(flnm) {
-  read_csv(flnm) %>% 
-    mutate(file_date = flnm)
+rt <-list()
+for (i in 1:length(fileList)) {
+  rt[[i]] <-read_csv(paste0(datapath, fileList[i])) %>%
+    mutate(file_date = gsub(".csv", "", fileList[i])) %>%
+    filter(type=="estimate") 
 }
 
-rt <-list.files(pattern = "*.csv", 
-             full.names = T) %>% 
-  map_df(~read_file_name(.) %>%
-           filter(type=="estimate") 
-  )
+rt <-do.call(bind_rows, rt)
 
 ####--- Pull midweek estimates and calculate means per date ---####
 
@@ -58,9 +50,9 @@ rt_med <-rt %>%
 
 ####--- Create phases---####
 
-rt3 <-function() {
+rt_phases <-function() {
   
-  rt3 <-rt_med %>%
+  rt_phases <-rt_med %>%
     ungroup() %>%
     rename(location_name=state) %>%
     group_by(location_name) %>%
@@ -85,12 +77,12 @@ rt3 <-function() {
     arrange(seq, groups_phase)
   
   # Pull first classifications from each group of phases & and create windows of every three groups
-  states <-c(unique(rt3$location_name))
+  states <-c(unique(rt_phases$location_name))
   df_phases <-list()
   
   for (i in 1:length(states)){
[…]

### 2023-04-18 Code/coverage.R

@@ -1,0 +1,21 @@
+library(tidyverse)
+
+coverage <-function(x, df) {
+  
+  obs_data <- read_csv("./Data/truth-Incident Cases.csv") %>%
+    mutate(wk_end_date = as.Date(date, "%m/%d/%y"),
+           wk_end_date=as.Date(cut(wk_end_date,"week", start.on.monday = FALSE)) + 6,
+           value=ifelse(value < 0, 0, value)) %>%
+    group_by(location_name, location, wk_end_date) %>%
+    summarize(true_value=sum(value)) %>%
+    rename(date=wk_end_date) %>%
+    arrange(location_name, date) %>%
+    rename(target_end_date=date)
+  
+  df <-df %>%
+    pivot_wider(names_from = c(type, quantile), values_from=value) %>%
+    left_join(., obs_data, by=c("location", "target_end_date")) %>%
+    mutate(coverage.50 = ifelse(true_value >= quantile_0.25 & true_value <= quantile_0.5, 1, 0),
+           coverage.80 = ifelse(true_value >= quantile_0.1 & true_value <= quantile_0.9, 1, 0),
+           coverage.95 = ifelse(true_value >= quantile_0.025 & true_value <= quantile_0.975, 1, 0))
+}

### 2023-04-18 Code/create_WIS.R

@@ -2,20 +2,27 @@ library(tidyverse)
 library(scoringutils)
 library(zoo)
 
-setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/")
-
 cut_date <-as.Date("2021-12-21")
 
 ####--- Observed data ---####
-source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/reported cases.R")
-obs_data <-rd_obs() %>%
-  dplyr::select(location_name, date, true_value)
+source("./Code/Reported cases.R")
+
+# obs_data <-reported_obs("state") %>%
+#   ungroup() %>%
+#   add_row(reported_obs("nation")) %>%
+#   add_state_names()
+
+obs_data <-reported_obs("county") %>%
+  mutate(location=as.numeric(location)) %>%
+  filter(location < 60000) %>%
+  mutate(location=as.character(location),
+         location=ifelse(nchar(location)==4, paste0("0",location), location))
 
 ####--- Estimate WIS ---####
 dat <-function() {
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
-  #load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
-  dat <-dat_US_state %>%  #dat_large_count %>% #
+  #load("./Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata")
+  load("./Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata")
+  dat <-dat_large_count %>% #dat_US_state %>%  #
     filter(sub_date <= cut_date)
   }
 
@@ -23,14 +30,13 @@ dat <-dat() %>%
   rename(date=target_end_date,
          prediction=value) %>%
   left_join(., obs_data, by=c("date", "location")) %>%
-  mutate(id=paste0(location, "_", date)) %>%
-  filter(!id %in% neg_or_zero$id)
+  neg_or_zero()
 
 WIS_all <-dat %>%
   filter(type=="quantile") %>%
-  dplyr::select(-forecast_date, -id) %>%
+  dplyr::select(-forecast_date) %>%
   score(.) %>%
   mutate(model=as.factor(model))
[…]

### 2023-04-18 Code/create_WIS_non large counties.R

@@ -2,18 +2,17 @@ library(tidyverse)
 library(scoringutils)
 library(zoo)
 
-setwd("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/")
 cut_date <-as.Date("2021-12-21")
 
 ####--- Observed data ---####
-source("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Code/Inc_Case_Eval_Manuscript/reported cases.R")
+source("./Code/Reported cases.R")
 obs_data <-rd_obs() %>%
   filter(nchar(location) > 2) %>%
   dplyr::select(location_name, date, true_value)
 
 ####--- Estimate WIS ---####
 dat <-function() {
-  load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")
+  load("./Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")
   dat <-dat_other_count %>%
     filter(sub_date <= cut_date)
 }
@@ -34,4 +33,4 @@ WIS_all <-dat %>%
   mutate(model=as.factor(model))
 WIS_all$model <-relevel(WIS_all$model, ref ="COVIDhub-baseline")
 
-save(WIS_all, file="WIS_all horizons_non large counties_all subs.rdata")
+save(WIS_all, file="./Data/WIS_all horizons_non large counties_all subs.rdata")

### 2023-05-16 Code/Manuscript_figures.Rmd
removed some commented out code

@@
   start_date <-as.Date("2020-07-28")
-  stop_date <-as.Date("2022-02-22")
 
   df <-df %>%
-    filter(sub_date >= start_date & sub_date <= cut_date) %>% #stop_date) %>%
+    filter(sub_date >= start_date & sub_date <= cut_date) %>% 
     dplyr::select(forecast_date, model, location, target, sub_date) %>%
@@
 
-#options(scipen = 999)
-
 # Function for WIS over time
@@
                Fig6.C, Fig6.F,
-             #Fig6.D, Fig6.H,
              ncol=2),
@@
 
-  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase")) %>% #, "cases_log_std[-2:2]")) %>%
+  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase")) %>% 
     rename(phase=x,

### 2023-05-16 Code/Supplement 2_CSSE revisions over time.R

@@ -56,8 +56,6 @@ states <-read.csv(here("Data/locations.csv")) %>%
   filter(nchar(fips)==2) %>%
   dplyr::select(abbreviation, location_name)
 
-#```{r Fig S2.1, echo=FALSE, warning=FALSE, message=FALSE, fig.height=12, fig.width=20}
-
 hx_dats_first <-hx_dats_all %>%
   mutate(geo_value=toupper(geo_value)) %>%
   left_join(., states, by=c("geo_value"="abbreviation")) %>%

### 2023-05-16 Code/create_WIS.R

@@ -6,17 +6,8 @@ cut_date <-as.Date("2021-12-21")
 
 ####--- Observed data ---####
 source("./Code/Reported cases.R")
-
-# obs_data <-reported_obs("state") %>%
-#   ungroup() %>%
-#   add_row(reported_obs("nation")) %>%
-#   add_state_names()
-
-obs_data <-reported_obs("county") %>%
-  mutate(location=as.numeric(location)) %>%
-  filter(location < 60000) %>%
-  mutate(location=as.character(location),
-         location=ifelse(nchar(location)==4, paste0("0",location), location))
+obs_data <-rd_obs() %>%
+  dplyr::select(location_name, date, true_value)
 
 ####--- Estimate WIS ---####
 dat <-function() {
@@ -30,7 +21,8 @@ dat <-dat() %>%
   rename(date=target_end_date,
          prediction=value) %>%
   left_join(., obs_data, by=c("date", "location")) %>%
-  neg_or_zero()
+  mutate(id=paste0(location, "_", date)) %>%
+  filter(!id %in% neg_or_zero$id)
 
 WIS_all <-dat %>%
   filter(type=="quantile") %>%

### 2023-12-18 Code/Supplement 1B_figures.Rmd
removed some commented out code
added rt data, updated figures

@@
 
-############################################################################
-############################################################################
-
 ```
@@
 ####
-load(here("Data/cases_county_forecasts_2022-04-04.Rdata"))
+load(here("Data/cases_county_forecasts.Rdata"))
 size <-read.csv(here("Data/SVI2018_US_COUNTY.csv")) %>%

### 2023-12-18 Code/Supplement 2_Outliers.Rmd
removed some commented out code
added rt data, updated figures

@@
 ## rename locations based on state names
-states <-read.csv(here("Data/locations.csv")) %>%
-  rename(fips = location) %>%
+states <-tidycensus::fips_codes %>% 
+  rename(fips = state_code, 
+         abbreviation=state, 
+         location_name=state_name) %>%
   mutate(fips = as.character(fips)) %>%
   filter(nchar(fips)==2) %>%
+  distinct() %>%
   dplyr::select(abbreviation, location_name)
@@
   #Phases
-  marg_means[[i]] <-ggemmeans(model_rev[[i]], terms=c("phase")) %>% #, "cases_log_std[-2:2]")) %>%
+  marg_means[[i]] <-as.data.frame(ggemmeans(model_rev[[i]], terms=c("phase")) %>% 
     rename(phase=x,
-           cases=group) %>%
+           cases=group))
+
+  marg_means[[i]] <-marg_means[[i]] %>%
 

### 2023-12-18 Code/Supplement 3.1_figure.rmd
added rt data, updated figures

@@
 cov.95 <-function() {
-  load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
+  load(here("Data/cases_large counties_forecasts_for analysis.rdata"))
 
@@
 
-  load(here("Data/cases_non large counties_forecasts_for analysis_2022-08-18.rdata"))
+  load(here("Data/cases_non large counties_forecasts_for analysis.rdata"))
 
@@
 
-load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
+load(here("Data/cases_large counties_forecasts_for analysis.rdata"))
 subs_co <-submissions(df=dat_large_count) %>%
@@
 
-load(here("Data/cases_non large counties_forecasts_for analysis_2022-08-18.rdata"))
+load(here("Data/cases_non large counties_forecasts_for analysis.rdata"))
 subs_co_other <-submissions(df=dat_other_count) %>%

### 2023-12-18 Code/Supplement 4_Spatial Correlations.Rmd
added rt data, updated figures

---
title: "Supplement 4: Spatial Correlations"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning=FALSE,message=FALSE)

library(here)
library(tidyverse)

library(scoringutils)
library(ggthemes)

library(sf)
library(spdep)

## Standardized formatting
strip.background_standard <-element_blank()
strip.text_standard <-element_text(size = 12, face='bold')
legend.text_standard <-element_text(size=12)
plot.caption_standard <-element_text(size=10, face = "italic")
axis.title.y_standard <-element_text(margin = margin(1, 10, 1, 1), size=12)
axis.text_standard <-element_text(size=11)

## Read in data used in analysis
load("./Data/WIS_all horizons_nat_state.rdata")
WIS_st <-WIS_all %>%
  ungroup() %>%
  filter(location_name!="National") %>%
  summarise_scores(by = c("model", "location_name"),
                   metric="interval_score",
                   relative_skill = TRUE,
                   baseline = "COVIDhub-baseline") %>%
  mutate(location_name=tolower(location_name)) %>%
  filter(model!="COVIDhub-baseline")

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

## Run Moran's I for spatial correlation of WIS estimates (states only)

set.seed(2354)

WIS_st$location_name <-str_to_title(WIS_st$location_name)
exclude <-c("Alaska", "Hawaii", "Puerto Rico")
coords <-tigris::states(class="sf", cb=TRUE) %>%
  mutate(NAME=str_to_title(NAME)) %>%
  dplyr::select(geometry, NAME) %>%
  filter(!NAME %in% exclude)

mods <-sort(unique(WIS_st$model))
MI <-list()

for(i in 1:length(mods)){
  WIS_st_sub <-WIS_st %>%
    dplyr::select(scaled_rel_skill, model, location_name) %>%
    filter(model==mods[i])

  s <-coords %>%
    left_join(., WIS_st_sub, by=c("NAME"="location_name")) %>%
    drop_na() %>%
    dplyr::select(-model)

  nb <-poly2nb(s, queen=TRUE) # Define the neighbors (use queen case)
  lw <-nb %>% nb2listw(., style="W", zero.policy=TRUE) # Compute the neighboring average WIS

  MI[[i]] <- moran.mc(s$scaled_rel_skill, lw, nsim=1000, alternative="greater") # Run the MC simulation version of the Moran's I test

}

MI_stat <-list()
MI_p <-list()
for(i in 1:length(mods)){
  MI_stat[[i]] <-MI[[i]]$statistic
  MI_p[[i]] <-MI[[i]]$p.value
}
stats <-round(do.call(c, MI_stat), 2)
ps <-round(do.call(c, MI_p), 3)

MI_results <-bind_cols(mods, stats, ps) %>%
  rename(model=1,
         morans=2, 
         p_value=3)

```

```{r Fig S4.1, echo=FALSE, warning=F, message=F, fig.height=8.5, fig.width=11}

### National WIS (for reordering teams in plot)
WIS_nat <-WIS_all %>%
  filter(location_name=="National") %>% 
  summarise_scores(by = c("model"),
                   metric="interval_score",
                   relative_skill = TRUE,
                   baseline = "COVIDhub-baseline") %>%
  left_join(., MI_results, by=c("model")) %>%
  filter(model!="COVIDhub-baseline") %>%
  mutate(order=paste0(model, "\nMoran's I: ", morans, " (p-value ", p_value, ")"),
         order=as.factor(ifelse(scaled_rel_skill < 1.0, paste0(model, "*\nMoran's I: ", morans, " (p-value ", p_value, ")"), order)),
         order=fct_reorder(order, scaled_rel_skill))
WIS_levels <-levels(WIS_nat$order) 
mods_better <-WIS_nat %>%
  filter(scaled_rel_skill < 1.0)

### Update map with Moran I's and reorder
us <-map_data("state")
WIS_map <-coords %>%
  left_join(., WIS_st, by=c("NAME"="location_name")) %>%
  left_join(., MI_results, by=c("model")) %>%
  mutate(model_group=ifelse(model %in% mods_better$model, "National rWIS < 1.0", "National rWIS > 1.0"), 
         model=ifelse(model %in% mods_better$model, paste0(model, "*"), model), 
         order=paste0(model, "\nMoran's I: ", morans, " (p-value ", p_value, ")"),
         order_fact=factor(order, levels=WIS_levels)) %>% drop_na()

WIS_map %>%
  ggplot(., aes(fill = log(scaled_rel_skill))) +
  geom_sf(color = "grey65") + 
  facet_wrap(~order_fact) +
  theme_void() +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 0, na.value = "grey75", 
                       name = "State-Level Relative\nWeighted Interval Score", 
                       breaks = c(-1,0,1,2), 
                       labels =c("0.5", 1, 2, 3)) + 
  labs(caption="*National rWIS < 1.0") +
  theme(plot.margin = unit(c(0,0,0,0), "cm"),
        strip.background=element_blank(), strip.text=element_text(size = 10, face='bold'),
        legend.justification = c(1,0), legend.position=c(0.90, 0.10),
        legend.direction = "horizontal")

```

### 2023-12-18 Code/Supplement 6_all figures.Rmd
added rt data, updated figures

--- 2023-04-18 Code/Supplement 5_all figures.Rmd
@@
 ---
-title: "Supplement 5"
+title: "Supplement 6"
 author: "VKL"
@@
 
-### Supplement 5: Horizon specific plots
+### Supplement 6: Horizon specific plots
 
@@
 
-load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.rdata"))
+load(here("Data/cases_nat_state_forecasts_for analysis.rdata"))
 
@@
 # Largest Counties
-load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
+load(here("Data/cases_large counties_forecasts_for analysis.rdata"))
 coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date,
@@
 
-```{r Fig S5.1, echo=FALSE, warning=F, message=F, fig.height=12, fig.width=12}
+```{r Fig S6.1, echo=FALSE, warning=F, message=F, fig.height=12, fig.width=12}
 
@@
 
-load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.rdata"))
-load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
+load(here("Data/cases_nat_state_forecasts_for analysis.rdata"))
+load(here("Data/cases_large counties_forecasts_for analysis.rdata"))
 
@@
 
-```{r Fig S5.2, echo=FALSE, warning=FALSE, message=FALSE, fig.height=11, fig.width=12}
+```{r Fig S6.2, echo=FALSE, warning=FALSE, message=FALSE, fig.height=11, fig.width=12}
 
@@
 
-```{r Fig S5.3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=15}
+```{r Fig S6.3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=15}
 

### 2023-12-18 Code/Supplement 7_figures.Rmd
added rt data, updated figures

--- 2023-04-18 Code/Supplement 6_figures.Rmd
@@
 ---
-title: "Supplement 6"
+title: "Supplement 7"
 author: "VKL"
@@
 
-### Supplement 6
+### Supplement 7
 
@@
 
-  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase", "cases_log_std[-1.96:1.96]")) %>%
+  marg_means[[i]] <-as.data.frame(ggemmeans(model[[i]], terms=c("phase", "cases_log_std[-1.96:1.96]")) %>%
     rename(phase=x,
-           cases=group) %>% 
+           cases=group))
+
+  marg_means[[i]] <-marg_means[[i]] %>% 
     mutate(model=team[i],
@@
 # Figure
-FigS6 <-marg_means %>%
+FigS7 <-marg_means %>%
   ggplot(., aes(cases_back_rescale, predicted_back_rescale)) +
@@
 
-```{r Fig s6, echo=FALSE, warning=F, message=F, fig.height=8, fig.width=11.5}
+```{r Fig S7, echo=FALSE, warning=F, message=F, fig.height=8, fig.width=11.5}
 
-grid.draw(shift_legend(FigS6))
+grid.draw(shift_legend(FigS7))
 

### 2023-12-18 Code/Supplement 4_Rt_Epi Phases.R

@@ -1,310 +1,0 @@
-library(tidyverse)
-library(zoo)
-library(data.table)
-library(mgcv)
-library(purrr)
-library(slider)
-
-####--- Read in Rt Data ---####
-
-## Need to update all file names since non alpha-numeric characters were included in the title (note, first needed to truncate names in the CMB with "ren *.* ??????????-test.*")
-datapath <-"./Data/epiforecasts_all_versions_rt/all_versions_exported/"
-fileList <-dir(path = datapath, pattern = '*.csv')  # list of file names, not including their paths
-
-rt <-list()
-for (i in 1:length(fileList)) {
-  rt[[i]] <-read_csv(paste0(datapath, fileList[i])) %>%
-    mutate(file_date = gsub(".csv", "", fileList[i])) %>%
-    filter(type=="estimate") 
-}
-
-rt <-do.call(bind_rows, rt)
-
-####--- Pull midweek estimates and calculate means per date ---####
-
-## Pick midweek estimates for all submissions
-rt <-rt %>%
-  mutate(median=as.numeric(median),
-         mean=as.numeric(mean),
-         sd=as.numeric(sd),
-         upper_90=as.numeric(upper_90),
-         lower_90=as.numeric(lower_90),
-         date=as.Date(date, "%m/%d/%Y"),
-         file_date=gsub(".csv","", file_date),
-         file_date=gsub("./","", file_date), 
-         state=ifelse(is.na(state), region, state),
-         wk_day=weekdays(as.Date(date))) %>%
-  filter(wk_day=="Wednesday",
-         state!="Northern Mariana Islands",
-         state!="Guam",
-         state!="American Samoa") %>%
-  dplyr::select(file_date, state, date, mean, median, lower_90, upper_90)
-
-
-## Median values per date
-rt_med <-rt %>%
-  group_by(state, date) %>%
-  summarize(median_med=median(median, na.rm=TRUE),
-            lower_90_med=median(lower_90, na.rm=TRUE),
-            upper_90_med=median(upper_90, na.rm=TRUE))
-
-####--- Create phases---####
-
-rt_phases <-function() {
-  
-  rt_phases <-rt_med %>%
-    ungroup() %>%
-    rename(location_name=state) %>%
-    group_by(location_name) %>%
-    
-    #Set up initial classifications
-    mutate(phase=ifelse(lower_90_med > 1.0, "increasing",
[…]

### 2023-12-18 Code/Supplement 5_Rt_Epi Phases.R

@@ -1,0 +1,333 @@
+library(tidyverse)
+library(zoo)
+library(data.table)
+library(mgcv)
+library(purrr)
+library(slider)
+
+####--- Read in Rt Data ---####
+
+## Need to update all file names since non alpha-numeric characters were included in the title (note, first needed to truncate names in the CMB with "ren *.* ??????????-test.*")
+datapath <-"./Data/rt estimates/"
+fileList <-dir(path = datapath, pattern = '*.csv')  # list of file names, not including their paths
+
+rt <-list()
+for (i in 1:length(fileList)) {
+  rt[[i]] <-read_csv(paste0(datapath, fileList[i])) %>%
+    mutate(file_date = gsub(".csv", "", fileList[i])) %>%
+    filter(type=="estimate") 
+}
+
+rt <-do.call(bind_rows, rt)
+
+####--- Pull midweek estimates and calculate means per date ---####
+
+## Pick midweek estimates for all submissions
+rt <-rt %>%
+  mutate(median=as.numeric(median),
+         mean=as.numeric(mean),
+         sd=as.numeric(sd),
+         upper_90=as.numeric(upper_90),
+         lower_90=as.numeric(lower_90),
+         date=as.Date(date, "%m/%d/%Y"),
+         file_date=gsub(".csv","", file_date),
+         file_date=gsub("./","", file_date), 
+         state=ifelse(is.na(state), region, state),
+         wk_day=weekdays(as.Date(date))) %>%
+  filter(wk_day=="Wednesday",
+         state!="Northern Mariana Islands",
+         state!="Guam",
+         state!="American Samoa") %>%
+  dplyr::select(file_date, state, date, mean, median, lower_90, upper_90)
+
+
+## Median values per date
+rt_med <-rt %>%
+  group_by(state, date) %>%
+  summarize(median_med=median(median, na.rm=TRUE),
+            lower_90_med=median(lower_90, na.rm=TRUE),
+            upper_90_med=median(upper_90, na.rm=TRUE))
+
+####--- Create phases---####
+
+rt_phases <-function() {
+  
+  rt_phases <-rt_med %>%
+    ungroup() %>%
+    rename(location_name=state) %>%
+    group_by(location_name) %>%
+    
+    #Set up initial classifications
+    mutate(phase=ifelse(lower_90_med > 1.0, "increasing",
[…]

### 2023-12-18 Code/pull_data_from_hub.R

@@ -1,0 +1,77 @@
+library(tidyverse)
+hubpath <- #To run code, insert locally cloned repository of the US COVID-19 Forecast Hub Repo  
+
+inclusion_dates <-seq(as.Date("2020-07-27"), as.Date("2021-12-20"), by="week") #Dates should be the Monday of the week since that's when forecast were due
+sec_models  <- c("CU-high", "CU-low","CU-mid","CU-nochange", "CU-scenario_high", "CU-scenario_low", "CU-scenario_mid",
+                 "COVIDhub-ensemble", "COVIDhub_CDC-ensemble") #Note ensemble replaced with 4_week ensemble
+selected_target <-paste0(seq(1:4), " wk ahead inc case") ## Selected targets
+
+all_dat <-list()
+filenames <-list()
+model_names <-list()
+dat_list <-list()
+for(i in 1:length(inclusion_dates)){
+  
+  date_to_pull <-inclusion_dates[i]-0:6
+  
+  datapath <-paste0(hubpath,"/data-processed") #Hubpath is a cloned repository of the US COVID-19 Forecast Hub Repo
+  
+  # CSV files to pull based on name and date range
+  filenames[[i]] <- c(list.files(path=datapath, pattern=as.character(date_to_pull[1]), 
+                              full.names = TRUE, recursive = TRUE),
+                   list.files(path=datapath, pattern=as.character(date_to_pull[2]), 
+                              full.names = TRUE, recursive = TRUE),
+                   list.files(path=datapath, pattern=as.character(date_to_pull[3]), 
+                              full.names = TRUE, recursive = TRUE),
+                   list.files(path=datapath, pattern=as.character(date_to_pull[4]), 
+                              full.names = TRUE, recursive = TRUE),
+                   list.files(path=datapath, pattern=as.character(date_to_pull[5]), 
+                              full.names = TRUE, recursive = TRUE),
+                   list.files(path=datapath, pattern=as.character(date_to_pull[6]), 
+                              full.names = TRUE, recursive = TRUE)
+    )
+  
+  exclude <-grep(paste(sec_models, collapse = "|"), filenames[[i]])
+  filenames[[i]] <-filenames[[i]][-c(exclude)] # Remove secondary models 
+  model_names[[i]] <-str_split(filenames[[i]], "/", simplify = TRUE)[ , 8]
+  
+  # Read in all submitted forecasts for week prior to date
+  dat_list[[i]] <-lapply(filenames[[i]],
[…]

### 2023-12-18 Code/Manuscript_figures.Rmd
Update Manuscript_figures.Rmd

--- 2023-04-18 Code/Manuscript_figures.Rmd
@@
 
+heatmap_format <-theme(axis.title.x = element_blank(), 
+                       axis.title.y = element_blank(), 
+                       axis.text=axis.text_standard,
+                       legend.position="bottom", legend.title.align=0.5, legend.box.just = "center")
+
 ```
@@
 
-load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))
+load(here("Data/cases_nat_state_forecasts_for analysis.Rdata"))
 
@@
   theme(axis.title.x = element_blank(), axis.text.y=element_text(angle=90, vjust=0.5, hjust=0.5),
-        legend.title = element_blank(), legend.position = c(0.20, 0.82)) + scale_y_continuous(label=comma,
-                                                                                               breaks=pretty_breaks(2))
+        legend.title = element_blank(), legend.position = c(0.20, 0.82)) + 
+  scale_y_continuous(label=comma, breaks=pretty_breaks(2))
+
 plot_grid(Fig1.A, Fig1.B,
@@
 
-Figure 2. 95% coverage and relWIS  and submissions per team
+### Figure 2. 95% coverage and relWIS  and submissions per team
 
@@
        title="B. Relative Weighted Interval Score") +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), axis.text.y=element_blank(),
-        axis.text=axis.text_standard,
-        legend.position="bottom")
+  heatmap_format + theme(axis.text.y=element_blank())
 
@@
 
-  load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))
+  load(here("Data/cases_nat_state_forecasts_for analysis.Rdata"))
 
@@
        title="C. 95% Coverage") +
-  theme(axis.title.x = element_blank(), #axis.text.x = element_text(angle = 45, hjust=1),
-        axis.title.y = element_blank(), axis.text.y=element_blank(),
-        axis.text=axis.text_standard,
-        legend.position="bottom")
+  heatmap_format + theme(axis.text.y=element_blank())
 
@@
        title="A. Percent of Weeks Submitted") +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text=axis.text_standard,
-        legend.position="bottom")
+  heatmap_format
 
@@
 # Figures
-load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))
+load(here("Data/cases_nat_state_forecasts_for analysis.Rdata"))
 
@@
 # Largest Counties
-load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata"))
+load(here("Data/cases_large counties_forecasts_for analysis.Rdata"))
 coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date))
@@
   labs(fill="Relative Weighted Interval Score") +
-  theme(axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1),
-        axis.title.y = element_blank(),
-        axis.text=axis.text_standard, plot.caption = plot.caption_standard)
+  heatmap_format +
+  theme(axis.text.x = element_text(angle = 45, hjust=1),
+        plot.caption = plot.caption_standard)
 
@@
 
-load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.Rdata"))
-load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.Rdata"))
+load(here("Data/cases_nat_state_forecasts_for analysis.Rdata"))
+load(here("Data/cases_large counties_forecasts_for analysis.Rdata"))
 
@@
 
-### Figure 7 . Marginal mean WIS
+### Figure 7 . Marginal mean WIS and 95% COverage
 
@@
 
-  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase")) %>% #, "cases_log_std[-2:2]")) %>%
+  marg_means[[i]] <-as.data.frame(ggemmeans(model[[i]], terms=c("phase")) %>% #, "cases_log_std[-2:2]")) %>%
     rename(phase=x,
-           cases=group) %>%
+           cases=group) 
+    )
+
+  marg_means[[i]] <-marg_means[[i]] %>%
 
@@
   theme(axis.title.y=axis.title.y_standard, axis.text.y=axis.text_standard,
-        legend.position = "bottom", legend.title = element_blank(), legend.text=legend.text_standard,
-        strip.text=strip.text_standard, strip.background=strip.background_standard,
         axis.title.x = element_blank(),
-        #axis.text.x = element_text(angle = 45, hjust=1),
         axis.text.x = element_blank())
@@
   theme_bw() +
-  theme(legend.position = "bottom", legend.title.align=0.5, legend.box.just = "center", 
-    plot.caption = plot.caption_standard,
-    strip.text=strip.text_standard, strip.background=strip.background_standard,
-    panel.border = element_rect(colour = "black", fill = NA),
-    axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust=1), axis.text=axis.text_standard,
+  heatmap_format +
+  theme(axis.text.x = element_blank(), #axis.text.x = element_text(angle = 45, hjust=1), 
       axis.ticks.y=element_blank())
@@
 
-```{r Fig7, echo=FALSE, warning=F, message=F, fig.height=8.5, fig.width=8.5}
+```{r echo=FALSE, warning=F, message=F}
 
-plot_grid(Fig7A, Fig7B, rel_heights  = c(0.5, 1), axis = "l",
-          align="v", nrow = 2)
+load(here("Data/WIS_all horizons_nat_state.rdata")) # data
+load("./Data/covid_epi_phases.rdata")
+
+Fig7C <-WIS_all %>%
+  filter(location!="US", 
+         range==95)%>%
+  dplyr::select( "location_name", "location", "target", "date", "model" ,
+                 "sub_date","coverage") %>% 
+  distinct() %>%
+  left_join(., phases, by=c("date", "location_name", "location")) %>%
+  drop_na() %>%
+  mutate(phase=str_to_title(phase)) %>%
+  mutate(model=as.factor(model),
+         model=factor(model, levels = levels),
+         phase=factor(phase, 
+                      levels = c("Increasing", "Peak", "Decreasing",  "Nadir")),
+         phase=fct_rev(phase)
+  ) %>%
+  group_by(phase, model) %>%
+  summarise(cov=round(mean(coverage), 2)) %>%
+  ggplot() +
+  geom_tile(aes(model, phase, fill=cov)) +
+  geom_text(aes(model, phase, label=cov), size=2.5) +
+  scale_fill_gradient2(low = "white", mid = "#f7fcb9", high = "#31a354", midpoint = 0.75, na.value = "grey75",
+                       name="95% Prediction Interval Coverage",
+                       guide = guide_colourbar(barheight = 1.5)) +
+  labs(y="", title="C.") + 
+  theme_bw() +
+  heatmap_format +
+  theme(panel.border = element_rect(colour = "black", fill = NA),
+        axis.text.x = element_text(angle = 45, hjust=1), 
+        axis.ticks.y=element_blank())
 
 ```
+
+```{r Fig7, echo=FALSE, warning=F, message=F, fig.height=11, fig.width=8.5}
+
+plot_grid(Fig7A, Fig7B, Fig7C,
+          rel_heights  = c(0.35, 0.50, 0.70), axis = "l",
+          align="v", nrow = 3)
+
+```
+
+### Figure 8: % Prediction in Each Direction
+
+```{r echo=FALSE, warning=F, message=F}
+
+#levels <-levels[!levels %in% "COVIDhub-baseline"]
+#
+dat <-dat_US_state %>%
+  filter(#!grepl("baseline", model), 
+         quantile==0.25 | quantile==0.75) %>%
+  pivot_wider(names_from = c(type, quantile), values_from=value)
+
+base <-dat_US_state %>%
+  filter(grepl("baseline", model),
+         quantile==0.5) %>%
+  pivot_wider(names_from = c(type, quantile), values_from=value) %>%
+  rename(quantile_0.50_base=quantile_0.5) %>%
+  dplyr::select(-model, -sub_date, -forecast_date)
+
+direct <-dat %>%
+  left_join(., base, by=c("location", "target", "target_end_date")) %>%
+  mutate(pred_class=as.factor(ifelse(quantile_0.25 > quantile_0.50_base, "increasing",
+                      ifelse(quantile_0.75 < quantile_0.50_base, "decreasing", "stable/uncertain")))) %>%
+  rename(date=target_end_date) %>%
+  left_join(., phases, by=c("date", "location")) %>%
+  drop_na() %>%
+  mutate(model=as.factor(model), 
+         model=factor(model, levels=levels),
+         phase=as.factor(str_to_title(phase)),
+         phase=factor(phase, levels=c("Nadir", "Decreasing", "Peak", "Increasing")))
+
+team_phase_pred <-crossing(direct$model, direct$pred_class, direct$phase) %>%
+  rename(model=1, 
+         pred_class=2,
+         phase=3) #%>%
+  #filter(!grepl("baseline", model))
+
+team_phase <-direct %>%
+  group_by(model, phase) %>%
+  count() %>%
+  rename(phase_denom=n)
+
+direct <-direct %>%
+  group_by(model, phase, pred_class) %>%
+  count(.) %>%
+  ungroup() %>%
+  right_join(., team_phase_pred, by=c("model", "phase", "pred_class")) %>%
+  left_join(., team_phase, by=c("model", "phase")) %>%
+  mutate(precent_pred=n/phase_denom, 
+         precent_pred=ifelse(is.na(precent_pred), 0, precent_pred), 
+         value_display=format(round(precent_pred, digits=2), nsmall = 2),
+         value_display=ifelse(value_display=="  NA", NA, value_display))
+
+Fig8A <-direct %>%
+  filter(pred_class=="increasing") %>%
+  ggplot(aes(model, phase)) +
+  geom_tile(aes(fill=precent_pred)) +
+  geom_text(aes(label=value_display), size=2.75) +
+  scale_fill_gradient2(low = "#fdd0a2", high = "#e6550d",  na.value = "grey75",
+                       name = stringr::str_wrap("Percent of forecasts with predicted increasing trajectory",
+                                                 width = 35), 
+                       guide = guide_colourbar(barheight = 1.5, title.position = "top")) +#, title.hjust=0.5)) +
+  labs(y="", title="A.") + 
+  theme_bw() +
+  heatmap_format +
+  theme(axis.text.x = element_blank(), 
+        axis.ticks.y=element_blank(), 
+        legend.position = "right", legend.direction = "horizontal", legend.title.align=0)
+
+Fig8B <-direct %>%
+  filter(pred_class=="stable/uncertain") %>%
+  ggplot(aes(model, phase)) +
+  geom_tile(aes(fill=precent_pred)) +
+  geom_text(aes(label=value_display), size=2.75) +
+  scale_fill_gradient2(low = "#dadaeb", high = "#54278f",  na.value = "grey75",
+                       name = stringr::str_wrap("Percent of forecasts with predicted stable or uncertain trajectory",
+                                                 width = 35), 
+                       guide = guide_colourbar(barheight = 1.5, title.position = "top")) +#, title.hjust=0.5)) +
+  labs(y="", title="B.") + 
+  theme_bw() +
+  heatmap_format +
+  theme(axis.text.x = element_blank(), 
+        axis.ticks.y=element_blank(), 
+        legend.position = "right", legend.direction = "horizontal", legend.title.align=0)
+
+Fig8C <-direct %>%
+  filter(pred_class=="decreasing") %>%
+  ggplot(aes(model, phase)) +
+  geom_tile(aes(fill=precent_pred)) +
+  geom_text(aes(label=value_display), size=2.75) +
+  scale_fill_gradient2(low = "#a1d99b", high = "#006d2c", na.value = "grey75",
+                       name = stringr::str_wrap("Percent of forecasts with predicted decreasing trajectory",
+                                                 width = 35), 
+                       guide = guide_colourbar(barheight = 1.5, title.position = "top")) +#, title.hjust=0.5)) +
+  labs(y="", title="C.") + 
+  theme_bw() +
+  heatmap_format +
+  theme(axis.text.x = element_text(angle = 45, hjust=1), 
+        axis.ticks.y=element_blank(), 
+        legend.position = "right", legend.direction = "horizontal", legend.title.align=0)
+
+```
+
+```{r Fig9, echo=FALSE, warning=F, message=F, fig.height=8.5, fig.width=11}
+
+plot_grid(Fig8A, Fig8B, Fig8C,
+          rel_heights  = c(0.50, 0.50, 0.82), axis = "l",
+          align="v", nrow = 3)
+
+```

### 2023-12-18 Code/Apply_inclusion_criteria.R
minor updates to data source

@@ -7,9 +7,7 @@ memory.limit(size = 50000)
 ### Inclusion criteria
 start_date <-as.Date('2020-07-28')
 stop_date <-as.Date('2021-12-21')
-
-## Non-primary models should be exlcuded
-sec_models <-c("CU-nochange",  "CU-scenario_high", "CU-scenario_low", "CU-scenario_mid", "COVIDhub_CDC-ensemble") #Note ensemble replaced with 4_week ensemble
+location_sub <-c("60", "66", "69")
 
 ## Must have 4 weeks of forecasts for all locations
 include_wks <-function(x, df){
@@ -77,30 +75,40 @@ include_subs <-function(x, df){
 
 ### Applying inclusion criteria
 
-## National
-load("./Data/updated_cases_nat_state_forecasts_2022-04-04.Rdata")
+## National/state
+load("./Data/submitted_cases_nat_state_forecasts.Rdata")
 
 dat_US_state <- all_dat %>%
+  
+  # Exclude weeks with missing missing prediction values
+  group_by(model, sub_date, target, location) %>%
+  filter(any(!is.na(value))) %>%
+  ungroup() %>%
 
   # inclusion criteria
-  filter(!(model %in% sec_models),
-         sub_date <= stop_date) %>%
+  filter(sub_date <= stop_date) %>%
   include_quant(df=.) %>%
   include_wks(df=.) %>%
   include_locs(df=.) %>%
   include_subs(df=.) %>%
-  dplyr::select(-quants, -no_horizons, -locs, -total, -subs, -percent_sub)
+  dplyr::select(-quants, -no_horizons, -locs, -total, -subs, -percent_sub) %>%
+  filter(!(location %in% location_sub)) #remove territories that few teams forecasted
 
-save(dat_US_state, file=paste0("./Data/cases_nat_state_forecasts_for analysis_",
-                               Sys.Date(), ".Rdata"))
+save(dat_US_state, file=paste0("./Data/cases_nat_state_forecasts_for analysis.Rdata"))
 
 ## Large counties
-load("./Data/cases_county_forecasts_2022-04-04.Rdata")
+load("./Data/Submitted_cases_county_forecasts.Rdata")
 
 # All inclusion criteria except for % of counties per pop size
 all_dat <-all_dat %>%
-  filter(!(model %in% sec_models),
-         sub_date <= stop_date) #%>%
+  
+  # exclude weeks with missing missing prediction values
[…]

### 2023-12-18 Code/create_WIS_non large counties.R

@@ -12,7 +12,7 @@ obs_data <-rd_obs() %>%
 
 ####--- Estimate WIS ---####
 dat <-function() {
-  load("./Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")
+  load("./Data/cases_non large counties_forecasts_for analysis.Rdata")
   dat <-dat_other_count %>%
     filter(sub_date <= cut_date)
 }

### 2023-12-21 Code/Supplement 1B_figures.Rmd
updated figure legends and text

--- 2023-04-18 Code/Supplement 1B_figures.Rmd
@@
    df <-df %>%
-     mutate(pop_size_quant2=ifelse(pop_size_quant2==1, "County Forecasts: Size Quantile 1",
-                                 ifelse(pop_size_quant2==2, "County Forecasts: Size Quantile 2",
-                                        ifelse(pop_size_quant2==3, "County Forecasts: Size Quantile 3", 
-                                               ifelse(pop_size_quant2==4, "County Forecasts: Size Quantile 4", "County forecasts: Size Quantile 5")))))
+     mutate(pop_size_quant2=ifelse(pop_size_quant2==1, "County Forecasts: Size Quintile 1",
+                                 ifelse(pop_size_quant2==2, "County Forecasts: Size Quintile 2",
+                                        ifelse(pop_size_quant2==3, "County Forecasts: Size Quintile 3", 
+                                               ifelse(pop_size_quant2==4, "County Forecasts: Size Quintile 4", "County forecasts: Size Quintile 5")))))
 }
@@
 ####
-load(here("Data/cases_county_forecasts_2022-04-04.Rdata"))
+load(here("Data/Submitted_cases_county_forecasts.Rdata"))
 size <-read.csv(here("Data/SVI2018_US_COUNTY.csv")) %>%

### 2023-12-21 Code/Supplement 3.1_figure.rmd
updated figure legends and text

@@
     distinct() %>%
-    mutate(pop_size_quant2="County Forecasts: Size Quantile 5",
+    mutate(pop_size_quant2="County Forecasts: Size Quintile 5",
            model_reorder=fct_reorder(model, scaled_rel_skill))
@@
     rename_counts() %>%
-    add_row(model="FRBSF_Wilson-Econometric", pop_size_quant2="County Forecasts: Size Quantile 1") %>% #,
-    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 1") %>% #, 
-    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 2") %>% #, 
-    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 3") %>% #, 
-    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 4") %>% 
+    add_row(model="FRBSF_Wilson-Econometric", pop_size_quant2="County Forecasts: Size Quintile 1") %>% #,
+    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quintile 1") %>% #, 
+    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quintile 2") %>% #, 
+    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quintile 3") %>% #, 
+    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quintile 4") %>% 
     mutate(model_reorder=model) %>%
@@
     summarize(mean_count=mean(coverage.95)) %>%
-    mutate(pop_size_quant2="County Forecasts: Size Quantile 5")
+    mutate(pop_size_quant2="County Forecasts: Size Quintile 5")
 
@@
   mutate(key=pop_size_quant2) %>%
-  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quantile 1") %>% #, 
-  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 1") %>% #, 
-  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 2") %>% #, 
-  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 3") %>% #, 
-  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 4") %>%
+  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quintile 1") %>% #, 
+  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 1") %>% #, 
+  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 2") %>% #, 
+  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 3") %>% #, 
+  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 4") %>%
   mutate(model_reorder=factor(model, levels_model))
@@
 subs_co <-submissions(df=dat_large_count) %>%
-  mutate(pop_size_quant2="County Forecasts: Size Quantile 5")
+  mutate(pop_size_quant2="County Forecasts: Size Quintile 5")
 
@@
   ungroup() %>%
-  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quantile 1") %>%  
-  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 1") %>% 
-  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 2") %>% 
-  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 3") %>% 
-  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 4") %>%
+  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quintile 1") %>%  
+  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 1") %>% 
+  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 2") %>% 
+  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 3") %>% 
+  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 4") %>%
   mutate(model_reorder=factor(model, levels_model)) %>%

### 2023-12-21 Code/Supplement 3.2 and 3.3_figures.rmd
updated figure legends and text

@@
 ### WIS Over time
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_non large counties_all subs.rdata")
+load(here("Data/WIS_all horizons_non large counties.rdata"))
 
@@
 ### Coverage Over time
-load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")
+load(here("Data/cases_non large counties_forecasts_for analysis.rdata"))
 
@@
 p1 <-cov.plot(coverage_count1, labels_count1) +
-  labs(title="County Forecasts: Size Quantile 1") +
+  labs(title="County Forecasts: Size Quintile 1") +
   theme(legend.position = c(0.02, 0.88), legend.title = element_blank(),
@@
 p2 <-cov.plot(coverage_count2, labels_count2) +
-  labs(title="County Forecasts: Size Quantile 2", 
+  labs(title="County Forecasts: Size Quintile 2", 
        y="")
@@
 p3 <-cov.plot(coverage_count3, labels_count3) +
-  labs(title="County Forecasts: Size Quantile 3",
+  labs(title="County Forecasts: Size Quintile 3",
        x="Expected Coverage")
@@
 p4 <-cov.plot(coverage_count4, labels_count4) +
-  labs(title="County Forecasts: Size Quantile 4",
+  labs(title="County Forecasts: Size Quintile 4",
        y="",

### 2023-12-21 Code/create_WIS_non large counties.R

@@ -33,4 +33,4 @@ WIS_all <-dat %>%
   mutate(model=as.factor(model))
 WIS_all$model <-relevel(WIS_all$model, ref ="COVIDhub-baseline")
 
-save(WIS_all, file="./Data/WIS_all horizons_non large counties_all subs.rdata")
+save(WIS_all, file="./Data/WIS_all horizons_non large counties.rdata")

### 2024-01-10 Code/Supplement 4_Spatial Correlations.Rmd
add caption to figure
per journal review request re copyright

@@
                        labels =c("0.5", 1, 2, 3)) + 
-  labs(caption="*National rWIS < 1.0") +
+  labs(caption="*National rWIS < 1.0\nThe base layer for this map was created with ggplot2 (https://ggplot2.tidyverse.org/reference/map_data.html).") +
   theme(plot.margin = unit(c(0,0,0,0), "cm"),
